---
title: "03_SYN_Exclusion"
author: "Chiara Draxler"
date: "29 3 2022"
output: html_document
---

#Introduction for working code:

0. Download the Code from Github. The new downloaded folder hc_switch_cccu-main contains the R project, Rmd Code, created data frames, knitted Html Code, Figures as .pdf and.jpg, Preregistered synthetic Code, and a folder to store the downloaded RData called RData.

Name the folder appropriately (when downloading the code from GitHub the folder will be hc_switch_cccu-main).

1. Download data from 
https://www.icpsr.umich.edu/web/DSDR/studies/37067/datadocumentation

Attention! The downloaded project from GitHub does not contain any data files!

--> Click on Download, then select R, then follow the login
--> store data in the folder specific to the R project in an extra sub-folder called RData (i.e., hc_switch_cccu-main - > RData). If you downloaded the code from GitHub, the RData folder will be already in the hc_switch_cccu-main projects folder.  

--> Within the RData folder store data for wave 1 in DS0001, for wave 2 in DS0002 and so on  (i.e., hc_switch_cccu-main - > RData -> DS0001 ). If you downloaded the code from GitHub, the relevant folders will be already there.

--> name the Rdata files according to the wave: 

Wave 1: 37067-0001-Data (i.e., hc_switch_cccu-main - > RData -> DS0001 -> 37067-0001-Data.rda )

Wave 2: 37067-0002-Data (i.e., hc_switch_cccu-main - > RData -> DS0002 -> 37067-0002-Data.rda )


Wave 3: 37067-0003-Data (i.e., hc_switch_cccu-main - > RData -> DS0003 -> 37067-0003-Data.rda )


Wave 4: 37067-0004-Data (i.e., hc_switch_cccu-main - > RData -> DS0004 -> 37067-0004-Data.rda )


--> attention to the .rda ending when loading the data into R!

2. make sure to install all relevant packages before running the code!

All relevant packages and versions can be seen in the section "Analyses"

3. run the code according to the defined order beginning with 01_ (or 0 if you want to have a look at the synthetic data) and ending with 09_ so that all data frames are created appropriately

4. Run  the Code :) 


#1. Load Data
```{r}
load("FAKE_cccu_complete1.RData")
```

#2. Load Packages

```{r}
library(dplyr)
library(formr)
library(ggplot2)
```

#3. Full Dataset
```{r}
nrow(FAKE_cccu_complete1) #timepoints
length(unique(FAKE_cccu_complete1$CASEID)) #women

```

##3.1 Exclude t4 from df (bc. not necessary)

```{r}
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
  filter(WAVE != "t4")
```



# 4 Building columns that indicate exclusion from df
1 = yes 

## 4.1 Missing Main Predictor: HC
Dont exclude current IUD & non-hormonal

```{r}
table(FAKE_cccu_complete1$hc)
table(is.na(FAKE_cccu_complete1$hc))

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_predHC = ifelse(is.na(hc), 1, 0))

table(FAKE_cccu_complete1$exclusion_missing_predHC)
FAKE_cccu_complete1$exclusion_missing_predHC <- as.factor(FAKE_cccu_complete1$exclusion_missing_predHC)
qplot(FAKE_cccu_complete1$exclusion_missing_predHC)

x = FAKE_cccu_complete1 %>%
  select(hc, exclusion_missing_predHC)
```

## 4.2 Missing Main Predictor: Satisfaction with HC


```{r}
table(FAKE_cccu_complete1$contra_satis) 
table(is.na(FAKE_cccu_complete1$contra_satis))

crosstabs( ~ is.na(contra_satis) + WAVE, data = FAKE_cccu_complete1)

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_pred_contra_satis = ifelse(is.na(contra_satis), 1, 0))

table(FAKE_cccu_complete1$exclusion_missing_pred_contra_satis)
FAKE_cccu_complete1$exclusion_missing_pred_contra_satis <- as.factor(FAKE_cccu_complete1$exclusion_missing_pred_contra_satis)
qplot(FAKE_cccu_complete1$exclusion_missing_pred_contra_satis)

x = FAKE_cccu_complete1 %>%
  select(contra_satis, exclusion_missing_pred_contra_satis)
```


## 4.3 Missing Main Predictor: Sex Freq & Sex Sat

```{r}
#sex freq
table(FAKE_cccu_complete1$sex_freq)
table(is.na(FAKE_cccu_complete1$sex_freq))

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_pred_sex_freq= ifelse(is.na(sex_freq), 1, 0))

table(FAKE_cccu_complete1$exclusion_missing_pred_sex_freq)
FAKE_cccu_complete1$exclusion_missing_pred_sex_freq <- as.factor(FAKE_cccu_complete1$exclusion_missing_pred_sex_freq)
qplot(FAKE_cccu_complete1$exclusion_missing_pred_sex_freq)

x = FAKE_cccu_complete1 %>%
  select(sex_freq, exclusion_missing_pred_sex_freq)

#sex_sat
table(FAKE_cccu_complete1$sexual_satisfaction)
table(is.na(FAKE_cccu_complete1$sexual_satisfaction))

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_pred_sex_sat= ifelse(is.na(sexual_satisfaction), 1, 0))

crosstabs( ~ is.na(sexual_satisfaction) + rel_dur_factor, data = FAKE_cccu_complete1)


table(FAKE_cccu_complete1$exclusion_missing_pred_sex_sat)#high missingness
FAKE_cccu_complete1$exclusion_missing_pred_sex_sat <- as.factor(FAKE_cccu_complete1$exclusion_missing_pred_sex_sat)
qplot(FAKE_cccu_complete1$exclusion_missing_pred_sex_sat)

x = FAKE_cccu_complete1 %>%
  select(sexual_satisfaction, exclusion_missing_pred_sex_sat)

```

## 4.4 Missing Selection Predictors
```{r}
#Age
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_age = as.factor(ifelse(is.na(AGE),1,0)))

table(is.na(FAKE_cccu_complete1$AGE))
table(FAKE_cccu_complete1$exclusion_missing_selection_age)
    
#Degree
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_degree = as.factor(ifelse(is.na(DEGREE_recode),1,0))) 
                                                             
table(is.na(FAKE_cccu_complete1$DEGREE_recode)) 
table(FAKE_cccu_complete1$exclusion_missing_selection_degree)

#Povrate
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_povrate= as.factor(ifelse(is.na(POVRATE),1,0))) 

table(is.na(FAKE_cccu_complete1$POVRATE))
table(FAKE_cccu_complete1$exclusion_missing_selection_povrate)

#Healthproblems
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_healthprb= as.factor(ifelse(is.na(HLTHPROB_recode),1,0))) 

table(is.na(FAKE_cccu_complete1$HLTHPROB_recode))
table(FAKE_cccu_complete1$exclusion_missing_selection_healthprb)#high missings

#Med Problems
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_medprob= as.factor(ifelse(is.na(MEDPROB_recode),1,0))) 

table(is.na(FAKE_cccu_complete1$MEDPROB_recode))
table(FAKE_cccu_complete1$exclusion_missing_selection_medprob)

#Gaps in insurance
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_gapins= as.factor(ifelse(is.na(GAPINS_recode),1,0))) 

table(is.na(FAKE_cccu_complete1$GAPINS_recode))
table(FAKE_cccu_complete1$exclusion_missing_selection_gapins)#missings

#Type of insurance
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_typeins= as.factor(ifelse(is.na(TYPEINS_recode),1,0))) 

table(is.na(FAKE_cccu_complete1$TYPEINS_recode))
table(FAKE_cccu_complete1$exclusion_missing_selection_typeins)#missings

#N Kids at T1
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_nkids= as.factor(ifelse(is.na(NKIDS_t1),1,0))) 

table(is.na(FAKE_cccu_complete1$NKIDS_t1))
table(FAKE_cccu_complete1$exclusion_missing_selection_nkids)#missings

#pregnant between waves
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_preg_bet_waves= as.factor(ifelse(is.na(pregnant_between_waves),1,0))) 

table(is.na(FAKE_cccu_complete1$pregnant_between_waves))
table(FAKE_cccu_complete1$exclusion_missing_selection_preg_bet_waves)#missings


#had baby between waves
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_baby_bet_waves= as.factor(ifelse(is.na(had_baby_between_waves),1,0))) 

table(is.na(FAKE_cccu_complete1$had_baby_between_waves))
table(FAKE_cccu_complete1$exclusion_missing_selection_baby_bet_waves)#missings


#Feel about pregnancy
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_feelpg= as.factor(ifelse(is.na(FEELPG_recode),1,0))) 

table(is.na(FAKE_cccu_complete1$FEELPG_recode))
table(FAKE_cccu_complete1$exclusion_missing_selection_feelpg)#high missings

#Avoidance of pregnancy
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_avoid= as.factor(ifelse(is.na(Avoid_r),1,0))) 

table(is.na(FAKE_cccu_complete1$Avoid_r))
table(FAKE_cccu_complete1$exclusion_missing_selection_avoid)#high missings

#Relationship duration
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_selection_reldur= as.factor(ifelse(is.na(rel_dur_factor),1,0))) 

table(is.na(FAKE_cccu_complete1$rel_dur_factor))
table(FAKE_cccu_complete1$exclusion_missing_selection_reldur)



#complete exclusion for all selection variables
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>% mutate(exclusion_missing_selection = as.factor(ifelse(is.na(AGE) | is.na(DEGREE_recode) | is.na(POVRATE)| is.na(HLTHPROB_recode) | is.na(MEDPROB_recode)| is.na(GAPINS_recode) | is.na(TYPEINS_recode) | is.na(NKIDS_t1) |is.na(pregnant_between_waves) | is.na(had_baby_between_waves) | is.na(FEELPG_recode) | is.na(Avoid_r) | is.na(rel_dur_factor), 1, 0)))

qplot(FAKE_cccu_complete1$exclusion_missing_selection)
table(FAKE_cccu_complete1$exclusion_missing_selection)

x = FAKE_cccu_complete1 %>%
  select(exclusion_missing_selection, exclusion_missing_selection_age, exclusion_missing_selection_degree, exclusion_missing_selection_povrate, exclusion_missing_selection_healthprb, exclusion_missing_selection_medprob, exclusion_missing_selection_gapins, exclusion_missing_selection_typeins, exclusion_missing_selection_nkids, exclusion_missing_selection_preg_bet_waves, exclusion_missing_selection_baby_bet_waves, exclusion_missing_selection_feelpg, exclusion_missing_selection_avoid, exclusion_missing_selection_reldur)
```


## 4.5 Missing Outcome (switch)
Dont exclude next IUD & non-hormonal
```{r}
table(FAKE_cccu_complete1$switch)
table(is.na(FAKE_cccu_complete1$switch))#high missingness


crosstabs( ~ is.na(switch) + WAVE, data = FAKE_cccu_complete1)

FAKE_cccu_complete1 %>% select(CASEID, WAVE, hc, hc_next, switch) %>% View()

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_outc_switch= ifelse(is.na(switch), 1, 0))

table(FAKE_cccu_complete1$exclusion_missing_outc_switch)
FAKE_cccu_complete1$exclusion_missing_outc_switch <- as.factor(FAKE_cccu_complete1$exclusion_missing_outc_switch)

qplot(FAKE_cccu_complete1$exclusion_missing_outc_switch)


x = FAKE_cccu_complete1 %>%
  select(switch, exclusion_missing_outc_switch)

```


## 4.6 Emergency contraception
```{r}
#overview

table(FAKE_cccu_complete1$EC_recode)

#create column that indicates if used EC

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
  mutate(exclusion_used_EC = ifelse(is.na(EC_recode), 0,
                                    ifelse(EC_recode == "No", 0,
                                           ifelse(EC_recode == "Yes", 1, NA))))

table(FAKE_cccu_complete1$exclusion_used_EC)
FAKE_cccu_complete1$exclusion_used_EC<- as.factor(FAKE_cccu_complete1$exclusion_used_EC)
qplot(FAKE_cccu_complete1$exclusion_used_EC)

```

## 4.7 IUD & Non-Hormonal
```{r}
table(FAKE_cccu_complete1$hc)
table(FAKE_cccu_complete1$IUD)

#IUD & non-hormonal 
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_IUD = ifelse(hc == "IUD&non_hc", 1,0)) 

table(FAKE_cccu_complete1$IUD)
table(FAKE_cccu_complete1$exclusion_IUD)
table(is.na(FAKE_cccu_complete1$exclusion_IUD))


table(FAKE_cccu_complete1$exclusion_IUD)
FAKE_cccu_complete1$exclusion_IUD<- as.factor(FAKE_cccu_complete1$exclusion_IUD)
qplot(FAKE_cccu_complete1$exclusion_IUD)

x = FAKE_cccu_complete1 %>%
  select(IUD, hc, exclusion_IUD)



#IUD_next & non-hormonal 

table(FAKE_cccu_complete1$hc_next)
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_IUD_next = ifelse(is.na(hc_next), 0,
                                    ifelse(hc_next == "non_hc" | hc_next == "hc", 0,
                                           ifelse(hc_next == "IUD&non_hc", 1, NA))))

table(FAKE_cccu_complete1$exclusion_IUD_next)
table(is.na(FAKE_cccu_complete1$exclusion_IUD_next))


table(FAKE_cccu_complete1$exclusion_IUD_next)
FAKE_cccu_complete1$exclusion_IUD_next<- as.factor(FAKE_cccu_complete1$exclusion_IUD_next)
qplot(FAKE_cccu_complete1$exclusion_IUD_next) #NA (missings) should be removed when excluding for missigness in hc or switch


x = FAKE_cccu_complete1 %>%
  select(CASEID, WAVE, IUD_next, hc_next, exclusion_IUD_next)
```
#column for complete exclusion process of main analysis
```{r}
#create column for complete exclusion process 
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>% mutate(exclusion_complete = as.factor(ifelse(exclusion_missing_predHC == 1 | exclusion_missing_pred_contra_satis ==1 | exclusion_missing_pred_sex_freq ==1 | exclusion_missing_pred_sex_sat ==1 | exclusion_missing_selection ==1 | exclusion_missing_outc_switch ==1 | exclusion_used_EC ==1| exclusion_IUD ==1 | exclusion_IUD_next ==1, 1, 0)))
```


## 4.8 Subanalyses Duration
### 4.8.1 non-hormonal contra
```{r}
table(FAKE_cccu_complete1$hc)

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_used_non_hc= ifelse(hc == "non_hc", 1,0))

table(FAKE_cccu_complete1$exclusion_used_non_hc)
table(is.na(FAKE_cccu_complete1$exclusion_used_non_hc))

FAKE_cccu_complete1$exclusion_used_non_hc<- as.factor(FAKE_cccu_complete1$exclusion_used_non_hc)
qplot(FAKE_cccu_complete1$exclusion_used_non_hc)


```

### 4.8.2 unknow duration


```{r}
table(FAKE_cccu_complete1$hc_dur)
table(is.na(FAKE_cccu_complete1$hc_dur))

crosstabs( ~ is.na(hc_dur) + sex_inlast30days, data = FAKE_cccu_complete1)

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
 mutate(exclusion_missing_pred_hc_dur= ifelse(is.na(hc_dur), 1, 0))

table(FAKE_cccu_complete1$exclusion_missing_pred_hc_dur)
FAKE_cccu_complete1$exclusion_missing_pred_hc_dur<- as.factor(FAKE_cccu_complete1$exclusion_missing_pred_hc_dur)
qplot(FAKE_cccu_complete1$exclusion_missing_pred_hc_dur)

x = FAKE_cccu_complete1 %>%
  select(hc_dur, exclusion_missing_pred_hc_dur)

```


## 4.9 Robustness analyses
### 4.9.1. No sex 
```{r}
table(FAKE_cccu_complete1$sex_inlast30days)#no sex in last 30 days

#create column that indicates with 1 = no sex and no contraceptive method used in last 30 days

FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
  mutate(exclusion_R1 = ifelse(is.na(sex_inlast30days), 0, 
                               ifelse(sex_inlast30days == "No", 1,
                                      ifelse(sex_inlast30days == "Yes", 0, NA))))

table(is.na(FAKE_cccu_complete1$exclusion_R1))
FAKE_cccu_complete1$exclusion_R1 <-as.factor(FAKE_cccu_complete1$exclusion_R1)
qplot(FAKE_cccu_complete1$exclusion_R1)#missingness might be because sex_inlast30days and NOBARRIER can be missing 

crosstabs(~hc + sex_inlast30days, data =FAKE_cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = No)

crosstabs(~exclusion_R1 + hc + NOBARRIER + sex_inlast30days, data =FAKE_cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = No)

```


### 4.9.2. Vasectomy
```{r}
#overview

table(FAKE_cccu_complete1$VASECTOMY)
table(FAKE_cccu_complete1$SP1VAS)
table(FAKE_cccu_complete1$SP2VAS)



#create column that indicates if used Vasectomy
FAKE_cccu_complete1 <- FAKE_cccu_complete1 %>%
  mutate(exclusion_R2 = ifelse(VASECTOMY == "(1) Yes" |
                                 SP1VAS == "(1) Yes" | SP2VAS == "(1) Yes", 1, NA),
         exclusion_R2 = ifelse(is.na(exclusion_R2), 0, exclusion_R2))
         

table(FAKE_cccu_complete1$exclusion_R2)
crosstabs(~exclusion_R2+ SP2VAS, data = FAKE_cccu_complete1)
FAKE_cccu_complete1$exclusion_R2 <-as.factor(FAKE_cccu_complete1$exclusion_R2)
qplot(FAKE_cccu_complete1$exclusion_R2)

```



# 5 Stepwise exclusion
## 5.1 Missing Main Predictor: HC
Dont exclude current IUD & non-hormonal
```{r}

#number of observations 
table(FAKE_cccu_complete1$exclusion_missing_predHC)

#exclude from df

FAKE_cccu_complete2 <-FAKE_cccu_complete1 %>%
  filter(exclusion_missing_predHC !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_predHC = 1 (might be combination with other exclusion criteria)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_predHC !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow() 

#0

length(unique(FAKE_cccu_complete2$CASEID)) #women
```


## 5.2 Missing Main Predictor: Satisfaction with HC
```{r}
#overview number of observations
table(FAKE_cccu_complete1$exclusion_missing_pred_contra_satis)

#exclude from df
FAKE_cccu_complete3 <-FAKE_cccu_complete2 %>%
  filter(exclusion_missing_pred_contra_satis !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_pred_contra_satis = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_pred_contra_satis !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#1188#high exclusion

length(unique(FAKE_cccu_complete3$CASEID)) #women
```


## 5.3 Missing Main Predictor: Sex Freq & Sex Sat

```{r}

#sex freq

#overview number of observations
table(FAKE_cccu_complete1$exclusion_missing_pred_sex_freq)

#exclude from df
FAKE_cccu_complete4 <-FAKE_cccu_complete3 %>%
  filter(exclusion_missing_pred_sex_freq !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_pred_sex_freq = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_pred_sex_freq !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()


#20
length(unique(FAKE_cccu_complete4$CASEID))

#sex satis
table(FAKE_cccu_complete1$exclusion_missing_pred_sex_sat)


#exclude from df
FAKE_cccu_complete5 <-FAKE_cccu_complete4 %>%
  filter(exclusion_missing_pred_sex_sat !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_pred_sex_sat = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_pred_sex_sat !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
3426-496

length(unique(FAKE_cccu_complete5$CASEID))

#469#high exclusion
```

## 5.4 Missing Selection Predictors
```{r}

#overview
table(FAKE_cccu_complete1$exclusion_missing_selection)

#exclude from df
FAKE_cccu_complete6<-FAKE_cccu_complete5 %>%
  filter(exclusion_missing_selection !=1)
length(unique(FAKE_cccu_complete6$CASEID))

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_selection = 1 (might be combination with other exclusion criteria)

#for alle selection predictors

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#306



#separate for all selection predictors:
#Age
table(FAKE_cccu_complete1$exclusion_missing_selection_age)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_age !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Degree
table(FAKE_cccu_complete1$exclusion_missing_selection_degree)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_degree !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Povrate
table(FAKE_cccu_complete1$exclusion_missing_selection_povrate)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_povrate !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Hlthprob
table(FAKE_cccu_complete1$exclusion_missing_selection_healthprb)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_healthprb !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#266#relatively high exclusion

#MedProb
table(FAKE_cccu_complete1$exclusion_missing_selection_medprob)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_medprob !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Gapins
table(FAKE_cccu_complete1$exclusion_missing_selection_gapins)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_gapins !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#24

#Typeins
table(FAKE_cccu_complete1$exclusion_missing_selection_typeins)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_typeins !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#24

#N kids at t1
table(FAKE_cccu_complete1$exclusion_missing_selection_nkids)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_nkids !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#15


#Preg between waves
table(FAKE_cccu_complete1$exclusion_missing_selection_preg_bet_waves)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_preg_bet_waves !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#6

#baby between waves
table(FAKE_cccu_complete1$exclusion_missing_selection_baby_bet_waves)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_baby_bet_waves !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#6

#Feelpg
table(FAKE_cccu_complete1$exclusion_missing_selection_feelpg)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_feelpg !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#16

#Avoid
table(FAKE_cccu_complete1$exclusion_missing_selection_avoid)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_avoid !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#14

#rel dur
table(FAKE_cccu_complete1$exclusion_missing_selection_reldur)
length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_selection_reldur !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0
```


## 5.5 Missing Outcome (switch)
Dont exclude next IUD & non-hormonal
```{r}
table(FAKE_cccu_complete1$exclusion_missing_outc_switch)
crosstabs(~exclusion_missing_outc_switch + WAVE, data = FAKE_cccu_complete1)

#exclude from df
FAKE_cccu_complete7 <-FAKE_cccu_complete6 %>%
  filter(exclusion_missing_outc_switch !=1)

length(unique(FAKE_cccu_complete7$CASEID))
#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_outc_switch = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_outc_switch !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#1427#high exclusion!



```

## 5.6 Emergency contraception
```{r}
table(FAKE_cccu_complete1$exclusion_used_EC)

#exclude from df
FAKE_cccu_complete8 <-FAKE_cccu_complete7 %>%
  filter(exclusion_used_EC !=1)

length(unique(FAKE_cccu_complete8$CASEID))

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_used_EC = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_used_EC !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0
```


## 5.7 IUD & Non-Hormonal
```{r}
#IUD 
table(FAKE_cccu_complete1$exclusion_IUD)

#exclude from df
FAKE_cccu_complete9 <-FAKE_cccu_complete8 %>%
  filter(exclusion_IUD !=1)
length(unique(FAKE_cccu_complete9$CASEID))
#number of excluded women from FAKE_cccu_complete1 bc of exclusion_IUD = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_IUD !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#402

#IUD next

table(FAKE_cccu_complete1$exclusion_IUD_next)

#exclude from df
FAKE_cccu_complete10 <-FAKE_cccu_complete9 %>%
  filter(exclusion_IUD_next !=1)

length(unique(FAKE_cccu_complete10$CASEID))

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_IUD_next = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_IUD_next !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#135

4634-1993
```

#rename df for Main Analysis 
```{r}
FAKE_cccu_MA <- FAKE_cccu_complete10
```


#save excluded sample for comparison included (FAKE_cccu_MA) vs excluded sample (FAKE_cccu_excluded)
```{r}
#save excluded sample 
FAKE_cccu_excluded <-FAKE_cccu_complete1 %>%
  filter(exclusion_complete ==1)

```


## 5.8 Subanalyses Duration
### 5.8.1 non-hormonal contra
```{r}
table(FAKE_cccu_complete1$exclusion_used_non_hc)


#exclude from df
FAKE_cccu_SA1 <-FAKE_cccu_MA %>%
  filter(exclusion_used_non_hc !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_used_non_hc = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_used_non_hc !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#2079#high exclusion
```

### 5.8.2 unknow duration
```{r}
table(FAKE_cccu_complete1$exclusion_missing_pred_hc_dur)

#exclude from df
FAKE_cccu_SA <-FAKE_cccu_SA1 %>%
  filter(exclusion_missing_pred_hc_dur !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_missing_pred_hc_dur = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_missing_pred_hc_dur !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#2580#high exclusion

length(unique(FAKE_cccu_SA$CASEID))
```

## 5.9 Robustness analyses
### 5.9.1. No sex
```{r}
table(FAKE_cccu_complete1$exclusion_R1)
#exclude from df
FAKE_cccu_R1<-FAKE_cccu_MA %>%
  filter(exclusion_R1 !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_R1 = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_R1 !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#656#relatively high exclusion
length(unique(FAKE_cccu_R1$CASEID))

#df for subanalysis
FAKE_cccu_R1_s<-FAKE_cccu_SA %>%
  filter(exclusion_R1 !=1)

```


### 5.9.2. Vasectomy
```{r}
table(FAKE_cccu_complete1$exclusion_R2)
#exclude from df
FAKE_cccu_R2<-FAKE_cccu_MA %>%
  filter(exclusion_R2 !=1)

#number of excluded women from FAKE_cccu_complete1 bc of exclusion_R2 = 1 (might be combination with other exclusion criteria)

length(unique(FAKE_cccu_complete1$CASEID)) -
  FAKE_cccu_complete1 %>%
  filter(exclusion_R2 !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#1

length(unique(FAKE_cccu_R2$CASEID))
#df for subanalysis
FAKE_cccu_R2_s<-FAKE_cccu_SA %>%
  filter(exclusion_R2 !=1)
```



#6 Save df

```{r}

#Main Analysis 


nrow(FAKE_cccu_MA) #timepoints
length(unique(FAKE_cccu_MA$CASEID)) #women

save(FAKE_cccu_MA,file = "FAKE_cccu_MA.RData")

load("FAKE_cccu_MA.RData")
##excluded sample
save(FAKE_cccu_excluded, file = "FAKE_cccu_excluded.RData")
load("FAKE_cccu_excluded.RData")


#Sub Analysis
save(FAKE_cccu_SA,file = "FAKE_cccu_SA.RData")

load("FAKE_cccu_SA.RData")

nrow(FAKE_cccu_SA) #timepoints
length(unique(FAKE_cccu_SA$CASEID)) #women



#R1
##MA
save(FAKE_cccu_R1,file = "FAKE_cccu_R1.RData")

load("FAKE_cccu_R1.RData")

nrow(FAKE_cccu_R1) #timepoints
length(unique(FAKE_cccu_R1$CASEID)) #women


##SA
save(FAKE_cccu_R1_s,file = "FAKE_cccu_R1_s.RData")

load("FAKE_cccu_R1_s.RData")

nrow(FAKE_cccu_R1_s) #timepoints
length(unique(FAKE_cccu_R1_s$CASEID)) #women

#R2
##MA
save(FAKE_cccu_R2,file = "FAKE_cccu_R2.RData")

load("FAKE_cccu_R2.RData")


nrow(FAKE_cccu_R2) #timepoints
length(unique(FAKE_cccu_R2$CASEID)) #women

##SA

save(FAKE_cccu_R2_s,file = "FAKE_cccu_R2_s.RData")

load("FAKE_cccu_R2_s.RData")
nrow(FAKE_cccu_R2_s) #timepoints
length(unique(FAKE_cccu_R2_s$CASEID)) #women
```

