---
title: "04_SYN_Codebook"
author: "Chiara Draxler"
date: "31 5 2022"
output: html_document
---

#Introduction for working code:

0. Download the Code from Github. The new downloaded folder hc_switch_cccu-main contains the R project, Rmd Code, created data frames, knitted Html Code, Figures as .pdf and.jpg, Preregistered synthetic Code, and a folder to store the downloaded RData called RData.

Name the folder appropriately (when downloading the code from GitHub the folder will be hc_switch_cccu-main).

1. Download data from 
https://www.icpsr.umich.edu/web/DSDR/studies/37067/datadocumentation

Attention! The downloaded project from GitHub does not contain any data files!

--> Click on Download, then select R, then follow the login
--> store data in the folder specific to the R project in an extra sub-folder called RData (i.e., hc_switch_cccu-main - > RData). If you downloaded the code from GitHub, the RData folder will be already in the hc_switch_cccu-main projects folder.  

--> Within the RData folder store data for wave 1 in DS0001, for wave 2 in DS0002 and so on  (i.e., hc_switch_cccu-main - > RData -> DS0001 ). If you downloaded the code from GitHub, the relevant folders will be already there.

--> name the Rdata files according to the wave: 

Wave 1: 37067-0001-Data (i.e., hc_switch_cccu-main - > RData -> DS0001 -> 37067-0001-Data.rda )

Wave 2: 37067-0002-Data (i.e., hc_switch_cccu-main - > RData -> DS0002 -> 37067-0002-Data.rda )


Wave 3: 37067-0003-Data (i.e., hc_switch_cccu-main - > RData -> DS0003 -> 37067-0003-Data.rda )


Wave 4: 37067-0004-Data (i.e., hc_switch_cccu-main - > RData -> DS0004 -> 37067-0004-Data.rda )


--> attention to the .rda ending when loading the data into R!

2. make sure to install all relevant packages before running the code!

All relevant packages and versions can be seen in the section "Analyses"

3. run the code according to the defined order beginning with 01_ (or 0 if you want to have a look at the synthetic data) and ending with 09_ so that all data frames are created appropriately

4. Run  the Code :) 
# Codebook {.tabset}
## 1. Packages and df
```{r}
library(ggplot2)
theme_set(theme_bw())
library(codebook)
library(tidyverse)
library(future)
library(psych)
library(Hmisc)
load("FAKE_FAKE_cccu_MA.RData")
```

## 2. Select data
```{r}
FAKE_cccu_MA = FAKE_cccu_MA %>%
  select(WAVE, switch, hc, contra_satis, hc_dur, sexual_satisfaction, sex_freq,
         AGE, DEGREE_recode, POVRATE, HLTHPROB_recode, MEDPROB_recode, GAPINS_recode, TYPEINS_recode, NKIDS_t1, pregnant_between_waves, had_baby_between_waves, Avoid_r, FEELPG_recode, rel_dur_factor)
```

## 3. Codebook
```{r}
codebook(FAKE_cccu_MA, missingness_report = FALSE, indent = "###")
```



#Plots


#Correlations

```{r}
#for t1
FAKE_cccu_MA_t1 <- FAKE_cccu_MA%>%
  filter(WAVE == "t1")
FAKE_cccu_MA_t1_correlations <- FAKE_cccu_MA_t1 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)


pairs.panels(FAKE_cccu_MA_t1_correlations, cex.cor = 10)

rcorr(as.matrix(FAKE_cccu_MA_t1_correlations))


#for t2
FAKE_cccu_MA_t2 <- FAKE_cccu_MA%>%
  filter(WAVE == "t2")

FAKE_cccu_MA_t2_correlations <- FAKE_cccu_MA_t2 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)
pairs.panels(FAKE_cccu_MA_t2_correlations, cex.cor = 10)
rcorr(as.matrix(FAKE_cccu_MA_t2_correlations))

#for t3
FAKE_cccu_MA_t3 <- FAKE_cccu_MA%>%
  filter(WAVE == "t3")

FAKE_cccu_MA_t3_correlations <- FAKE_cccu_MA_t3 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)

pairs.panels(FAKE_cccu_MA_t3_correlations, cex.cor = 10)

rcorr(as.matrix(FAKE_cccu_MA_t3_correlations))
```

