---
title: "15_SYN_Plots"
author: "Chiara Draxler & Laura Botzet"
date: "24 1 2022"
output: html_document
---

## 1. Load Data
```{r}
# load("FAKE_cccu_MA.RData")
# load("FAKE_cccu_SA.RData")
# length(unique(FAKE_cccu_SA$CASEID)) #women
# load("FAKE_cccu_R1.RData")
# load("FAKE_cccu_R2.RData")
# load("FAKE_cccu_R1_s.RData")
# length(unique(FAKE_cccu_R1_s$CASEID)) #women
# load("FAKE_cccu_R2_s.RData")
```


## 2. Load Packages
```{r}
library(formr)
library(brms)
library(marginaleffects)
library(sjPlot)
library(tidyverse)


set.seed(180822)

set_priors <- c(prior(normal(0, 1), class = b),
                prior(normal(0, 1), class = sd))
options(scipen=999)

apatheme = theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line()
  ) +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
```


## 3. Specific effects
Plots for
- hc*contra_satis
- hc*sexual_satisfaction
- hc*sex_freq
- hc_dur*contra_satis
based on multilevel model FAKE_m3
```{r}
FAKE_m3 <- brm(file = "models/FAKE_m3.Rds")

### contra_satis

contra_satis <- plot_model(FAKE_m3, type = "pred",
                           terms = c("contra_satis", "hc"),
                           ci.lvl = 0.997) +
  scale_fill_manual(
    values = c("red", "blue"),
    name = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    ),
  ) +
  scale_colour_manual(
    values = c("red", "blue"),
    name  = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    )
  ) +
  labs(y = "Probability to Switch", title = "") +
  scale_x_discrete("Contraceptive Satisfaction",
                   limits = c("1", "2", "3", "4")) +
  apatheme

contra_satis

ggsave("contra_satis.pdf", contra_satis)

ggsave("contra_satis.png", contra_satis)

#contra satis on FAKE_m2
FAKE_m2 <- brm(file = "models/FAKE_m2.Rds")

contra_satis_FAKE_m2 <- plot_model(FAKE_m2, type = "pred",
                           terms = c("contra_satis", "hc"),
                           ci.lvl = 0.997) +
  scale_fill_manual(
    values = c("red", "blue"),
    name = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    ),
  ) +
  scale_colour_manual(
    values = c("red", "blue"),
    name  = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    )
  ) +
  labs(y = "Probability to Switch", title = "") +
  scale_x_discrete("Contraceptive Satisfaction",
                   limits = c("1", "2", "3", "4")) +
  apatheme

contra_satis_FAKE_m2

ggsave("contra_satis_FAKE_m2.pdf", contra_satis_FAKE_m2)

ggsave("contra_satis_FAKE_m2.png", contra_satis_FAKE_m2)


###sexual satisfaction

sex_sat <- plot_model(FAKE_m3, type = "pred", terms = c("sexual_satisfaction", "hc"), ci.lvl = 0.997)  +  
  scale_fill_manual(
    values = c("red", "blue"),
    name = "Group",
    breaks = c("hc", "non_hc"),
     labels = c(
      "HC",
      "Non-HC"
    ),
  ) +
  scale_colour_manual(
    values = c("red", "blue"),
    name  = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    )
  ) +
  labs(y = "Probability to Switch", title = "") +
  scale_x_discrete("Sexual Satisfaction",
                   limits = c("1", "2", "3", "4", "5", "6")) +
  apatheme
sex_sat

ggsave("sexual_satis.pdf", sex_sat)

ggsave("sexual_satis.png", sex_sat)

###sexual frequency

sex_freq <- plot_model(FAKE_m3, type = "pred", terms = c("sex_freq", "hc"), ci.lvl = 0.997)  +
  scale_fill_manual(
    values = c("red", "blue"),
    name = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    ),
  ) +
  scale_colour_manual(
    values = c("red", "blue"),
    name  = "Group",
    breaks = c("hc", "non_hc"),
    labels = c(
      "HC",
      "Non-HC"
    )
  ) +
  labs(y = "Probability to Switch", title = "") +
  scale_x_discrete("Sexual Frequency",
                   limits = c("No sex or once", "2-5 times","6-10 times", "11 or more times"), guide = guide_axis(n.dodge=2)) +
  apatheme
sex_freq

ggsave("sexual_freq.pdf", sex_freq)

ggsave("sexual_freq.png", sex_freq)

#for hc dur  in sub analyses

sa_FAKE_m3 <- brm(file = "models/sa_FAKE_m3.Rds")


hc_dur<-
  plot_model(sa_FAKE_m3, type = "pred",  show.legend = TRUE,
             terms = c("contra_satis","hc_dur[0, 12,24,36,48]"), ci.lvl = 0.997) +
  labs(y = "Probability to Switch", title = "") +
  scale_x_discrete("Contraceptive Satisfaction",
                   limits = c("1", "2", "3", "4"))+
  scale_color_discrete(name = "Duration", labels = c("< 1 year",
                                                     "1-2 years",
                                                     "2-3 years",
                                                     "3-4 years",
                                                     ">4 years")) +
  apatheme

hc_dur





ggsave("hc_dur.pdf", hc_dur)

ggsave("hc_dur.png", hc_dur)


```



## 4. Forest plot main effects
for models FAKE_m1, FAKE_m2, FAKE_m3, FAKE_m4

### Models
#### FAKE_m1
```{r}
FAKE_FAKE_m1 <- brm(file = "models/FAKE_FAKE_m1.Rds")

FAKE_FAKE_m1_sum = summary(FAKE_FAKE_m1, prob = .997)
```

#### FAKE_m1 in robustness analyses
```{r}
####1 Robustness analyses : FAKE_m1 
FAKE_R1_ma_1 <- brm(file = "models/FAKE_R1_ma_1.Rds")
FAKE_R1_FAKE_m1_sum = summary(FAKE_R1_ma_1, prob = .997)

####2 Robustness analyses: FAKE_m1 
FAKE_R2_ma_1 <- brm(file = "models/FAKE_R2_ma_1.Rds")

FAKE_R2_FAKE_m1_sum = summary(FAKE_R2_ma_1, prob = .997)

```


#### FAKE_m2
```{r}
FAKE_m2 <- brm(file = "models/FAKE_m2.Rds")
FAKE_m2_sum = summary(FAKE_m2, prob = .997)
```

#### FAKE_m2 in robustness analyses 
```{r}
#r1
FAKE_R1_ma_2 <- brm(file = "models/FAKE_R1_ma_2.Rds")

FAKE_R1_FAKE_m2_sum = summary(FAKE_R1_ma_2, prob = .997)

#r2
FAKE_R2_ma_2 <- brm(file = "models/FAKE_R2_ma_2.Rds")
FAKE_R2_FAKE_m2_sum = summary(FAKE_R2_ma_2, prob = .997)

```

#### FAKE_m3
```{r}
FAKE_m3 <- brm(file = "models/FAKE_m3.Rds")
FAKE_m3_sum = summary(FAKE_m3, prob = .997)
```

#### FAKE_m3 in robustness analyses 
```{r}
#r1
FAKE_R1_ma_3 <- brm(file = "models/FAKE_R1_ma_3.Rds")

FAKE_R1_FAKE_m3_sum = summary(FAKE_R1_ma_3, prob = .997)

#r2
FAKE_R2_ma_3 <- brm(file = "models/FAKE_R2_ma_3.Rds")
FAKE_R2_FAKE_m3_sum = summary(FAKE_R2_ma_3, prob = .997)
```



#### FAKE_m4
```{r}
FAKE_m4 = brm(file = "models/FAKE_m4.Rds")
FAKE_m4_sum <- summary(FAKE_m4, prob = .997)
```

#### FAKE_m4 in robustness analysis 
```{r}
#r1
FAKE_R1_ma_4 <- brm(file = "models/FAKE_R1_ma_4.Rds")

FAKE_R1_FAKE_m4_sum = summary(FAKE_R1_ma_4, prob = .997)

#r2
FAKE_R2_ma_4 <- brm(file = "models/FAKE_R2_ma_4.Rds")

FAKE_R2_FAKE_m4_sum = summary(FAKE_R2_ma_4, prob = .997)
```


### Effects and CIs
#### FAKE_m1
```{r}
FAKE_m1_forest_plot = FAKE_m1_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("model_1", 2)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_m1_forest_plot) = c()
```

#### FAKE_m1 in Robustnessanalyses
```{r}
#R1
FAKE_R1_FAKE_m1_forest_plot = FAKE_R1_FAKE_m1_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_model_1", 2)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_FAKE_m1_forest_plot) = c()

#R2
FAKE_R2_FAKE_m1_forest_plot = FAKE_R2_FAKE_m1_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_model_1", 2)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_FAKE_m1_forest_plot) = c()

```


#### FAKE_m2
```{r}
FAKE_m2_forest_plot = FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_m2_forest_plot) = c()
```


#### FAKE_m2 in robustness analyses
```{r}
#R1
FAKE_R1_FAKE_m2_forest_plot = FAKE_R1_FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_FAKE_m2_forest_plot) = c()


#R2
FAKE_R2_FAKE_m2_forest_plot = FAKE_R2_FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_FAKE_m2_forest_plot) = c()
```




#### FAKE_m3
```{r}
FAKE_m3_forest_plot = FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("model_3", 12)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_m3_forest_plot) = c()
```

#### FAKE_m3 in Robustnessanalyses
```{r}
#R1
FAKE_R1_FAKE_m3_forest_plot = FAKE_R1_FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_model_3", 12)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_FAKE_m3_forest_plot) = c()

#R2
FAKE_R2_FAKE_m3_forest_plot = FAKE_R2_FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_model_3", 12)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_FAKE_m3_forest_plot) = c()

```






#### FAKE_m4
```{r}
FAKE_m4_forest_plot = FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("model_4", 72)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_m4_forest_plot) = c()
```

#### FAKE_m4 in Robustnessanalyses
```{r}
#R1
FAKE_R1_FAKE_m4_forest_plot = FAKE_R1_FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_model_4", 72)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_FAKE_m4_forest_plot) = c()

#R2
FAKE_R2_FAKE_m4_forest_plot = FAKE_R2_FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_model_4", 72)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_FAKE_m4_forest_plot) = c()

```



###Forest plot without robustness analyses
#### Dataframe for plot
```{r}
#without robustness analyses
forest_plot_data = rbind(
  FAKE_m1_forest_plot,
  FAKE_m2_forest_plot,
  FAKE_m3_forest_plot,
  FAKE_m4_forest_plot
)

forest_plot_data$predictor = factor(forest_plot_data$predictor,
                                    levels = c("Intercept",
                                               "hcnon_hc",
                                               "contra_satis",
                                               "hcnon_hc:contra_satis",
                                               "sexual_satisfaction","hcnon_hc:sexual_satisfaction",
                                  
                                               "sex_freq2M5times", "sex_freq6FAKE_m10times",
                                               "sex_freq11ormoretimes", 
                                                            "hcnon_hc:sex_freq2M5times",
                                               "hcnon_hc:sex_freq6FAKE_m10times",
                                               "hcnon_hc:sex_freq11ormoretimes"),
                                    labels = c("(Intercept)",
                                               "HC",
                                               "Contraceptive Satisfaction",
                                               "HC:Contraceptive Satisfaction",
                                               "Sexual Satisfaction","HC:Sexual Satisfaction",    
                                               "Sexual Frequency 2-5 times", "Sexual Frequency 6-10 times",
                                               "Sexual Frequency 11 or more times",
                                                                                          "HC:Sexual Frequency 2-5 times",
                                               "HC:Sexual Frequency 6-10 times",
                                               "HC:Sexual Frequency 11 or more times"))

forest_plot_data$group = factor(
  forest_plot_data$group,
  levels = 
    c(
    "model_1",
    "model_2",
    "model_3",
    "model_4"
  ),
  labels = 
    c(
    "model_1",
    "model_2",
    "model_3",
    "model_4"
  )
)


#give group for color:
forest_plot_data <- forest_plot_data%>%
  mutate(grouping = ifelse(group == "model_1" , "color_1",
  ifelse(group == "model_2" , "color_2",
        ifelse(group == "model_3", "color_3",
                ifelse(group == "model_4" ,"color_4",NA))))) 
```

#### Plot
```{r}
#forest plot without robustness analyses

#set colors
group.color <- c("orchid3", "green", "blue", "red")

#set names for facets
grouping_names = c("Model 1", "Model 2", "Model 3", "Model 4")
names(grouping_names) = c("color_1", "color_2", "color_3", "color_4")

forest_ma <- ggplot(
  data = forest_plot_data %>%
    filter(predictor != "(Intercept)"),
  aes(
    x = predictor,
    y = estimate,
    group = forcats::fct_rev(grouping),
    fill = forcats::fct_rev(grouping),
    color = forcats::fct_rev(grouping),
    shape = grouping
  )
) +
  geom_point(position = position_dodge(width = 0.8)) +
  geom_pointrange(aes(ymin = lower, ymax = upper),
                  position = position_dodge(width = 0.8)) +
  scale_x_discrete(limits = rev) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  scale_fill_manual(
    name = "Models",
    breaks = c("color_1", "color_2", "color_3", "color_4"),
    labels = 
      c(
      "Model 1",
      "Model 2",
      "Model 3",
      "Model 4"
    ),
    values = group.color
  ) +
  scale_colour_manual(
    name = "Models",
    breaks = c("color_1", "color_2", "color_3", "color_4"),
    labels = c(
      "Model 1",
      "Model 2",
      "Model 3",
      "Model 4"
    ),
    values = group.color
  ) +
  scale_shape_manual(
    name = "Models",
    values = c(21,24,22,25),
    labels = c(
      "Model 1",
      "Model 2",
      "Model 3",
      "Model 4"
    )
  ) +
  labs(y = "Effect Size", x = "Predictor") +
  apatheme

forest_ma

ggsave("forest_ma.pdf", forest_ma, width = 23, height = 12, units = "cm", dpi = 300)
ggsave("forest_ma.png", forest_ma, width = 23, height = 12, units = "cm", dpi = 300)

```



### Forest plot with robustness analyses
#### Dataframe for plot
```{r}
#for robustness analyses
forest_plot_data2 = rbind(
  FAKE_m1_forest_plot,
  FAKE_R1_FAKE_m1_forest_plot,
  FAKE_R2_FAKE_m1_forest_plot,
  FAKE_m2_forest_plot,
  FAKE_R1_FAKE_m2_forest_plot,
  FAKE_R2_FAKE_m2_forest_plot,
  FAKE_m3_forest_plot,
  FAKE_R1_FAKE_m3_forest_plot,
  FAKE_R2_FAKE_m3_forest_plot,
  FAKE_m4_forest_plot,
  FAKE_R1_FAKE_m4_forest_plot,
  FAKE_R2_FAKE_m4_forest_plot
)

forest_plot_data2$predictor = factor(forest_plot_data2$predictor,
                                    levels = c("Intercept",
                                               "hcnon_hc",
                                               "contra_satis",
                                               "hcnon_hc:contra_satis",
                                               "sexual_satisfaction","hcnon_hc:sexual_satisfaction",
                                  
                                               "sex_freq2M5times", "sex_freq6FAKE_m10times",
                                               "sex_freq11ormoretimes", 
                                                            "hcnon_hc:sex_freq2M5times",
                                               "hcnon_hc:sex_freq6FAKE_m10times",
                                               "hcnon_hc:sex_freq11ormoretimes"),
                                    labels = c("(Intercept)",
                                               "\nHC\n",
                                               "Contraceptive Satisfaction",
                                               "HC:Contraceptive Satisfaction",
                                               "Sexual Satisfaction","HC:Sexual Satisfaction",    
                                               "Sexual Frequency 2-5 times", "Sexual Frequency 6-10 times",
                                               "Sexual Frequency 11 or more times",
                                                                                          "HC:Sexual Frequency 2-5 times",
                                               "HC:Sexual Frequency 6-10 times",
                                               "HC:Sexual Frequency 11 or more times"))

forest_plot_data2$group = factor(
  forest_plot_data2$group,
  levels = 
    c(
    "model_1",
    "FAKE_R1_model_1",
    "FAKE_R2_model_1",
    "model_2",
    "FAKE_R1_model_2",
    "FAKE_R2_model_2",
    "model_3",
    "FAKE_R1_model_3",
    "FAKE_R2_model_3",
    "model_4",
    "FAKE_R1_model_4",
    "FAKE_R2_model_4"
    ),
  labels = 
    c(
    "model_1",
    "FAKE_R1_model_1",
    "FAKE_R2_model_1",
    "model_2",
    "FAKE_R1_model_2",
    "FAKE_R2_model_2",
    "model_3",
    "FAKE_R1_model_3",
    "FAKE_R2_model_3",
    "model_4",
    "FAKE_R1_model_4",
    "FAKE_R2_model_4"
  )
)


#give group for color:
forest_plot_data2 <- forest_plot_data2 %>%
  mutate(grouping = ifelse(group == "model_1" |group == "FAKE_R1_model_1" | group == "FAKE_R2_model_1", "color_1",
  ifelse(group == "model_2" |group == "FAKE_R1_model_2" | group == "FAKE_R2_model_2", "color_2",
         ifelse(group == "model_3" |group == "FAKE_R1_model_3" | group == "FAKE_R2_model_3", "color_3",
                 ifelse(group == "model_4" |group == "FAKE_R1_model_4" | group == "FAKE_R2_model_4",
                        "color_4", NA))))) 


#give group for shape:
forest_plot_data2 <- forest_plot_data2 %>%
  mutate(shape = ifelse(group ==  "model_1"|
  group == "model_2" |
    group == "model_3"|
    group == "model_4", "shape_1",
  ifelse(group %contains% "R1", "shape_2",
         ifelse(group %contains% "R2", "shape_3", NA))))

```

#### Plot
```{r forest_ma_ra, fig.height = 30, fig.width = 60}
#forest plot including robustness analyses

#set colors
group.color <- c("orchid3", "green", "blue")

#set names for facets
grouping_names = c("Model 1", "Model 2", "Model 3", "Model 4")
names(grouping_names) = c("color_1", "color_2", "color_3", "color_4")

forest_ma_ra <- ggplot(
  data = forest_plot_data2 %>%
    filter(predictor != "(Intercept)"),
  aes(
    x = predictor,
    y = estimate,
    group = forcats::fct_rev(shape),
    fill = forcats::fct_rev(shape),
    color = forcats::fct_rev(shape),
    shape = shape
  )
) +
  geom_point(position = position_dodge(width = 0.8)) +
  geom_pointrange(aes(ymin = lower, ymax = upper),
                  position = position_dodge(width = 0.8)) +
  scale_x_discrete(limits = rev) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  scale_fill_manual(
    name = "Analyses",
    breaks = c("shape_1", "shape_2", "shape_3"),
    labels = 
      c(
      "Main Analyses",
      "Robustness Analyses 1",
      "Robustness Analyses 2"
    ),
    values = group.color
  ) +
  scale_colour_manual(
    name = "Analyses",
    breaks = c("shape_1", "shape_2", "shape_3"),
    labels = c(
      "Main Analyses",
      "Robustness Analyses 1",
      "Robustness Analyses 2"
    ),
    values = group.color
  ) +
  scale_shape_manual(
    name = "Analyses",
    values = c(21,24,22),
    labels = c(
      "Main Analyses",
      "Robustness Analyses 1",
      "Robustness Analyses 2"
    )
  ) +
  labs(y = "Effect Size", x = "Predictor") +
  facet_wrap(~grouping,
             labeller = labeller(grouping = grouping_names)) +
  apatheme +
  theme(
    axis.text = element_text(size = 30),
    axis.title = element_text(size = 30),
    legend.text = element_text(size = 30),
    legend.title = element_text(size = 30),
    strip.text = element_text(size=30)
  )

forest_ma_ra

ggsave("forest_ma_ra.pdf", forest_ma_ra, width = 60, height = 30, units = "cm", dpi = 300)
ggsave("forest_ma_ra.png", forest_ma_ra, width = 60, height = 30, units = "cm", dpi = 300)

```






## 5. Forest Plot Sub Analyses

### Model
#### FAKE_m2
```{r}
sa_FAKE_m2 <- brm(file = "models/sa_FAKE_m2.Rds")

sa_FAKE_m2_sum<- summary(sa_FAKE_m2, prob = .997)
```

#### FAKE_m2 in robustness analyses 
```{r}
FAKE_R1_sa_FAKE_m2 <- brm(file = "models/FAKE_R1_sa_FAKE_m2.Rds")

FAKE_R1_sa_FAKE_m2_sum<- summary(FAKE_R1_sa_FAKE_m2, prob = .997)

FAKE_R2_sa_FAKE_m2 <- brm(file = "models/FAKE_R2_sa_FAKE_m2.Rds")

FAKE_R2_sa_FAKE_m2_sum<- summary(FAKE_R2_sa_FAKE_m2, prob = .997)

```



#### FAKE_m3
```{r}
sa_FAKE_m3 <- brm(file = "models/sa_FAKE_m3.Rds")

sa_FAKE_m3_sum<- summary(sa_FAKE_m3, prob = .997)

```


#### FAKE_m3 in robustness analyses 
```{r}
FAKE_R1_sa_FAKE_m3 <- brm(file = "models/FAKE_R1_sa_FAKE_m3.Rds")

FAKE_R1_sa_FAKE_m3_sum<- summary(FAKE_R1_sa_FAKE_m3, prob = .997)

FAKE_R2_sa_FAKE_m3 <- brm(file = "models/FAKE_R2_sa_FAKE_m3.Rds")

FAKE_R2_sa_FAKE_m3_sum<- summary(FAKE_R2_sa_FAKE_m3, prob = .997)
```



#### FAKE_m4
```{r}
sa_FAKE_m4 <- brm(file = "models/sa_FAKE_m4.Rds")

sa_FAKE_m4_sum <- summary(sa_FAKE_m4, prob = .997)
```

#### FAKE_m4 in robustnessanalyses
```{r}
FAKE_R1_sa_FAKE_m4 <- brm(file = "models/FAKE_R1_sa_FAKE_m4.Rds")

FAKE_R1_sa_FAKE_m4_sum<- summary(FAKE_R1_sa_FAKE_m4, prob = .997)

FAKE_R2_sa_FAKE_m4 <- brm(file = "models/FAKE_R2_sa_FAKE_m4.Rds")

FAKE_R2_sa_FAKE_m4_sum<- summary(FAKE_R2_sa_FAKE_m4, prob = .997)
```



### Effects and CIs

#### FAKE_m2
```{r}
sa_FAKE_m2_forest_plot = sa_FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("sa_model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(sa_FAKE_m2_forest_plot) = c()
```


#### FAKE_m2 in robustness analyses
```{r}
#R1
FAKE_R1_sa_FAKE_m2_forest_plot = FAKE_R1_sa_FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_sa_model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_sa_FAKE_m2_forest_plot) = c()


#R2
FAKE_R2_sa_FAKE_m2_forest_plot = FAKE_R2_sa_FAKE_m2_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_sa_model_2", 4)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_sa_FAKE_m2_forest_plot) = c()

```




#### FAKE_m3
```{r}
sa_FAKE_m3_forest_plot = sa_FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("sa_model_3", 8)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(sa_FAKE_m3_forest_plot) = c()
```

#### FAKE_m3 in Robustnessanalyses
```{r}
#R1
FAKE_R1_sa_FAKE_m3_forest_plot = FAKE_R1_sa_FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_sa_model_3", 8)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_sa_FAKE_m3_forest_plot) = c()

#R2
FAKE_R2_sa_FAKE_m3_forest_plot = FAKE_R2_sa_FAKE_m3_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_sa_model_3", 8)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_sa_FAKE_m3_forest_plot) = c()

```






#### FAKE_m3
```{r}
sa_FAKE_m4_forest_plot = sa_FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("sa_model_4", 37)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(sa_FAKE_m4_forest_plot) = c()
```

#### FAKE_m3 in Robustnessanalyses
```{r}
#R1
FAKE_R1_sa_FAKE_m4_forest_plot = FAKE_R1_sa_FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R1_sa_model_4", 37)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R1_sa_FAKE_m4_forest_plot) = c()

#R2
FAKE_R2_sa_FAKE_m4_forest_plot = FAKE_R2_sa_FAKE_m4_sum$fixed %>%
  data.frame() %>%
  mutate(predictor = rownames(.),
         group = rep("FAKE_R2_sa_model_4", 37)) %>%
  select(predictor,
         estimate = Estimate,
         lower = l.99.7..CI,
         upper = u.99.7..CI,
         group)

rownames(FAKE_R2_sa_FAKE_m4_forest_plot) = c()

```

### Forest plot without robustness analyses


#### Dataframe for plot
```{r}
#without robustness analyses
sa_forest_plot_data = rbind(
  sa_FAKE_m2_forest_plot,
  sa_FAKE_m3_forest_plot,
  sa_FAKE_m4_forest_plot
)

sa_forest_plot_data$predictor = factor(sa_forest_plot_data$predictor,
                                    levels = c("Intercept",
                                               "contra_satis",
                                               "hc_dur",
                                               "contra_satis:hc_dur",
                                               "sexual_satisfaction",
                                               "sex_freq2M5times", "sex_freq6FAKE_m10times",
                                               "sex_freq11ormoretimes"),
                                    labels = c("(Intercept)",
                                               "Contraceptive Satisfaction",
                                               "Duration",
                                               "Contraceptive Satisfaction:Duration",
                                               "Sexual Satisfaction",  
                                               "Sexual Frequency 2-5 times", "Sexual Frequency 6-10 times",
                                               "Sexual Frequency 11 or more times")) 

sa_forest_plot_data$group = factor(
  sa_forest_plot_data$group,
  levels = 
    c(
    "sa_model_2",
    "sa_model_3",
    "sa_model_4"
  ),
  labels = 
    c(
    "sa_model_2",
    "sa_model_3",
    "sa_model_4"
  )
)


#give group for color:
sa_forest_plot_data <- sa_forest_plot_data %>%
  mutate(grouping =   ifelse(group == "sa_model_2" , "color_2",
         ifelse(group == "sa_model_3"  ,"color_3",
                 ifelse(group == "sa_model_4" , "color_4",NA)))) 



```

#### Plot
```{r}
#forest plot without robustness analyses

#set colors
group.color <- c("green", "blue", "red")

forest_sa <- ggplot(
  data = sa_forest_plot_data %>%
    filter(predictor != "(Intercept)"),
  aes(
    x = predictor,
    y = estimate,
    group = forcats::fct_rev(grouping),
    fill = forcats::fct_rev(grouping),
    color = forcats::fct_rev(grouping),
    shape = grouping
  )
) +
  geom_point(position = position_dodge(width = 0.9),
             alpha = 0.08) +
  geom_pointrange(aes(ymin = lower, ymax = upper),
                  position = position_dodge(width = 0.9)) +
  scale_x_discrete(limits = rev, expand = c(0.002, 0)) +
  # scale_y_continuous(limits = c(-8,8),
  #                    breaks = seq(-8,8,2)) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  scale_fill_manual(
    name = "Models",
    breaks = c("color_2", "color_3", "color_4"),
    labels = 
      c(
      "Model 2",
      "Model 3",
      "Model 4"
    ),
    values = group.color
  ) +
  scale_colour_manual(
    name = "Models",
    breaks = c("color_2", "color_3", "color_4"),
    labels = 
      c(
      "Model 2",
      "Model 3",
      "Model 4"
    ),
    values = group.color
  ) +
  scale_shape_manual(
    name = "Models",
    values = c(21,24,22),
    labels = c(
      "Model 2",
      "Model 3",
      "Model 4"
    )
  ) +
  labs(y = "Effect Size", x = "Predictor") +
  apatheme

forest_sa

ggsave("forest_sa.pdf", forest_sa, width = 23, height = 12, units = "cm", dpi = 300)
ggsave("forest_sa.png", forest_sa, width = 23, height = 12, units = "cm", dpi = 300)

```



### Forest plot with robustness analyses
#### Dataframe for plot
```{r}
#for robustness analyses
sa_forest_plot_data2 = rbind(
  sa_FAKE_m2_forest_plot,
  FAKE_R1_sa_FAKE_m2_forest_plot,
  FAKE_R2_sa_FAKE_m2_forest_plot,
  sa_FAKE_m3_forest_plot,
  FAKE_R1_sa_FAKE_m3_forest_plot,
  FAKE_R2_sa_FAKE_m3_forest_plot,
  sa_FAKE_m4_forest_plot,
  FAKE_R1_sa_FAKE_m4_forest_plot,
  FAKE_R2_sa_FAKE_m4_forest_plot
)

sa_forest_plot_data2$predictor = factor(sa_forest_plot_data2$predictor,
                                    levels = c("Intercept",
                                               "contra_satis",
                                               "hc_dur",
                                               "contra_satis:hc_dur",
                                               "sexual_satisfaction",
                                               "sex_freq2M5times", "sex_freq6FAKE_m10times",
                                               "sex_freq11ormoretimes"),
                                    labels = c("(Intercept)",
                                               "Contraceptive Satisfaction",
                                               "Duration",
                                               "Contraceptive Satisfaction:Duration",
                                               "Sexual Satisfaction",  
                                               "Sexual Frequency 2-5 times", "Sexual Frequency 6-10 times",
                                               "Sexual Frequency 11 or more times")) 

sa_forest_plot_data2$group = factor(
  sa_forest_plot_data2$group,
  levels = 
    c(
    "sa_model_2",
    "FAKE_R1_sa_model_2",
    "FAKE_R2_sa_model_2",
    "sa_model_3",
    "FAKE_R1_sa_model_3",
    "FAKE_R2_sa_model_3",
    "sa_model_4",
    "FAKE_R1_sa_model_4",
    "FAKE_R2_sa_model_4"
  ),
  labels = 
    c(
    "sa_model_2",
    "FAKE_R1_sa_model_2",
    "FAKE_R2_sa_model_2",
    "sa_model_3",
    "FAKE_R1_sa_model_3",
    "FAKE_R2_sa_model_3",
    "sa_model_4",
    "FAKE_R1_sa_model_4",
    "FAKE_R2_sa_model_4"
  )
)


#give group for color:
sa_forest_plot_data2 <- sa_forest_plot_data2 %>%
  mutate(grouping = ifelse(group == "sa_model_2" |group == "FAKE_R1_sa_model_2" | group == "FAKE_R2_sa_model_2",
                           "color_2",
         ifelse(group == "sa_model_3" |group == "FAKE_R1_sa_model_3" | group == "FAKE_R2_sa_model_3",
                "color_3",
                 ifelse(group == "sa_model_4" |group == "FAKE_R1_sa_model_4" | group == "FAKE_R2_sa_model_4",
                        "color_4",NA)))) 


#give group for shape:
sa_forest_plot_data2 <- sa_forest_plot_data2 %>%
  mutate(shape = ifelse(group == "sa_model_2" |
    group == "sa_model_3"|
    group == "sa_model_4", "shape_1",
  ifelse(group %contains% "R1", "shape_2",
         ifelse(group %contains% "R2", "shape_3", NA))))

```

#### Plot
```{r forest_sa_ra, fig.height = 30, fig.width = 60}
#forest plot including robustness analyses

#set colors
group.color <- c("orchid3", "green", "blue")

#set names for facets
grouping_names = c("Model 1", "Model 2", "Model 3", "Model 4")
names(grouping_names) = c("color_1", "color_2", "color_3", "color_4")

forest_sa_ra <- ggplot(
  data = sa_forest_plot_data2 %>%
    filter(predictor != "(Intercept)"),
  aes(
    x = predictor,
    y = estimate,
    group = forcats::fct_rev(shape),
    fill = forcats::fct_rev(shape),
    color = forcats::fct_rev(shape),
    shape = shape
  )
) +
  geom_point(position = position_dodge(width = 0.6)) +
  geom_pointrange(aes(ymin = lower, ymax = upper),
                  position = position_dodge(width = 0.6)) +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(breaks = c(-1,0,1), limits = c(-1.5, 1.5)) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  scale_fill_manual(
    name = "Analyses",
    breaks = c("shape_1", "shape_2", "shape_3"),
    labels = 
      c(
      "Sub Analyses",
      "Robustness Sub Analyses 1",
      "Robustness Sub Analyses 2"
    ),
    values = group.color
  ) +
  scale_colour_manual(
    name = "Analyses",
    breaks = c("shape_1", "shape_2", "shape_3"),
    labels = c(
      "Sub Analyses",
      "Robustness Sub Analyses 1",
      "Robustness Sub Analyses 2"
    ),
    values = group.color
  ) +
  scale_shape_manual(
    name = "Analyses",
    values = c(21,24,22),
    labels = c(
      "Sub Analyses",
      "Robustness Sub Analyses 1",
      "Robustness Sub Analyses 2"
    )
  ) +
  labs(y = "Effect Size", x = "Predictor") +
  facet_wrap(~grouping,
             labeller = labeller(grouping = grouping_names)) +
  apatheme +
  theme(
    axis.text = element_text(size = 24),
    axis.title = element_text(size = 24),
    legend.text = element_text(size = 24),
    legend.title = element_text(size = 24),
    strip.text = element_text(size=24)
  )

forest_sa_ra

ggsave("forest_sa_ra.pdf", forest_sa_ra, width = 40, height = 20, units = "cm", dpi = 300)
ggsave("forest_sa_ra.png", forest_sa_ra, width = 60, height = 30, units = "cm", dpi = 300)
```
