---
title: "01_Data_Import"
author: "Chiara Draxler"
date: "22 12 2021"
output: html_document
---


##Introduction for working code:

0. Select a folder specific for the R project and define to use the folder for the R project constantly (when downloading the code from GitHub the folder will be hc_switch_cccu-main)

1. Download data from 
https://www.icpsr.umich.edu/web/DSDR/studies/37067/datadocumentation

--> Click on Download, then select R, then follow the login
--> store data in the folder specific to the R project in an extra sub-folder called RData (i.e., hc_switch_cccu-main - > RData)

--> Within the RData folder store data for wave 1 in DS0001, for wave 2 in DS0002 and so on  (i.e., hc_switch_cccu-main - > RData -> DS0001 )

--> name the Rdata files according to the wave: 

Wave 1: 37067-0001-Data (i.e., hc_switch_cccu-main - > RData -> DS0001 -> 37067-0001-Data.rda )

Wave 2: 37067-0002-Data (i.e., hc_switch_cccu-main - > RData -> DS0002 -> 37067-0002-Data.rda )


Wave 3: 37067-0003-Data (i.e., hc_switch_cccu-main - > RData -> DS0003 -> 37067-0003-Data.rda )


Wave 4: 37067-0004-Data (i.e., hc_switch_cccu-main - > RData -> DS0004 -> 37067-0004-Data.rda )


--> attention to the .rda ending when loading the data into R!

2. make sure to install all relevant packages before running the code!

All relevant packages and versions can be seen in the section "Analyses"

3. run the code according to the defined order beginning with 01_ (or 0 if you want to have a look at the synthetic data) and ending with 09_ so that all data frames are created appropriately

4. Run  the Code :) 



#1. Loading Data 

```{r}
load("RData/DS0001/37067-0001-Data.rda")
cccu_wave1 = da37067.0001

load("RData/DS0002/37067-0002-Data.rda")
cccu_wave2 = da37067.0002

load("RData/DS0003/37067-0003-Data.rda")
cccu_wave3 = da37067.0003

load("RData/DS0004/37067-0004-Data.rda")
cccu_wave4 = da37067.0004
```

#2. Loading Packages
```{r}
#loading package plyr
library("plyr")
#loading dplyr
library("dplyr")
```

#3. Create column WAVE to indicate wave
Because it is the simplest to just add WAVE and t1-t4 for the waves 

```{r}
#create column in each df
cccu_wave1$WAVE <- 't1'

#check
table(cccu_wave1$WAVE)#correct

cccu_wave2$WAVE<- 't2'
cccu_wave3$WAVE <- 't3'
cccu_wave4$WAVE <- 't4'


```

#4. Connect datasets via rowbind (to get in longitudinal format)
```{r}
#check column names
colnames(cccu_wave1)
colnames(cccu_wave2)
colnames(cccu_wave3)
colnames(cccu_wave4)

#we have different columns in every df --> we can use rbind.fill from plyr, which works as follows:  "If a column exists in both data frames, it is row binded as usual. However, if a column is missing in one of the two data frames, the empty cells are replaced by NA" (https://statisticsglobe.com/rbind-in-r-example-vector-data-frame-fill-columns/)


#binding rows of the df via rbind.fill from plyr
cccu_complete <- rbind.fill(cccu_wave1, cccu_wave1)

#binding the all four df to complete dataframe:
cccu_complete <- rbind.fill(cccu_wave1, cccu_wave2, cccu_wave3, cccu_wave4)

#checking rows and CASEID 
nrow(cccu_wave1)+nrow(cccu_wave2)+nrow(cccu_wave3)+nrow(cccu_wave4)
nrow(cccu_complete)#true

which(cccu_complete$CASEID == 81, arr.ind=TRUE)#CaseID exists four times!

##we now have a complete df with up to 4 observations per particpant and binded columns (or new columns, if they did not exist before)
```
#5. Saving Data
```{r}
save(cccu_complete,file = "cccu_complete.RData")

load("cccu_complete.RData")
```


