---
title: "03_Exclusion"
author: "Chiara Draxler"
date: "21 1 2022"
output: html_document
---

- Ausschluss von Vpn
•	-  Main Analyses:
•	- No Morning after pill
•	- No missingness in:
•	- Switch
•	- Method satisfaction
•	- Sex satisfaction
•	- Sex freq
•	- selection variables
•	sum(is.na()) > 0
•	- Duration Analyses: 
•	Hauptausschluss + only Hc-user + no missing duration
•

#1. Load Data
```{r}

load("Fake_cccu_complete1.RData")
```

#2. Load Packages

```{r}
library(dplyr)
```

#3. Main Analysis 

##3.1 No morning after pill

```{r}
#overview

table(Fake_cccu_complete1$EC_recode)

#create column that indicates if used EC

Fake_cccu_complete1 <- Fake_cccu_complete1 %>%
  mutate(exclusion_used_EC = ifelse(EC_recode == "Yes",1,0))

#overview, factorize and plot

table(Fake_cccu_complete1$exclusion_used_EC)

Fake_cccu_complete1$exclusion_used_EC<-as.factor(Fake_cccu_complete1$exclusion_used_EC)


plot(Fake_cccu_complete1$exclusion_used_EC)

#exclude from df

#create df: exclude women following exclusion_R1 from the maindf 

Fake_cccu_main_analysis <-Fake_cccu_complete1 %>%
  filter(exclusion_used_EC != 1) 

#check

table(Fake_cccu_main_analysis$exclusion_used_EC)

```

##3.2 No missingness
in:

•	- No missingness in:
•	- Switch
•	- Method satisfaction
•	- Sex satisfaction
•	- Sex freq
•	- selection variables
•	sum(is.na()) > 0

```{r}
table(Fake_cccu_complete1$switch)
sum(is.na(Fake_cccu_complete1$switch))
#create column that indicates missingness in relevant variables

Fake_cccu_complete1 <- Fake_cccu_complete1 %>%
 mutate(exclusion_missingness = ifelse(sum
                                       (is.na(Fake_cccu_complete1$switch)+
                                        is.na(Fake_cccu_complete1$sexual_satisfaction)+
                                           is.na(Fake_cccu_complete1$sex_freq)+
                                           is.na(Fake_cccu_complete1$AGE)+
                                           is.na(Fake_cccu_complete1$DEGREE_recode)+
                                           is.na(Fake_cccu_complete1$POVRATE)+
                                           is.na(Fake_cccu_complete1$HLTHPROB_recode)+
                                           is.na(Fake_cccu_complete1$MEDPROB_recode)+
                                                                                      is.na(Fake_cccu_complete1$GAPINS_recode)+
                                           is.na(Fake_cccu_complete1$TYPEINS_recode)+
                                           is.na(Fake_cccu_complete1$NKIDS_t1)+
                                           is.na(Fake_cccu_complete1$pregnant_between_waves)+
                                                                                      is.na(Fake_cccu_complete1$had_baby_between_waves)+
                                           is.na(Fake_cccu_complete1$FEELPG_recode)+
                                                                                      is.na(Fake_cccu_complete1$Avoid_recode)+
                                           is.na(Fake_cccu_complete1$rel_dur_factor))>0, 1, 0)) 

table(Fake_cccu_complete1$exclusion_missingness)



```


#4. Subanalysis
 no missingness in contraceptive duration and df only for hc user
 
```{r}

```
 
 
#5. Analysis of robustness

##5.1 Analysis of robustness 1
```{r}
#overview over relevant variables

table(Fake_cccu_complete1$NOBARRIER)#no non-hormonal contraceptive method in last 30days
table(Fake_cccu_complete1$hc)#no hormonal contracepive method 
#joint = no contraceptive method 

table(Fake_cccu_complete1$sex_inlast30days)#no sex in last 30 days

#create column that indicates with 1 = no sex and no contraceptive method used in last 30 days

Fake_cccu_complete1 <- Fake_cccu_complete1 %>%
  mutate(exclusion_R1 = ifelse(NOBARRIER == "(1) Yes" & 
                                 hc == "non_hc" &
                                 sex_inlast30days == "No",1,0))

table(Fake_cccu_complete1$exclusion_R1)

crosstabs(~exclusion_R1 + hc + NOBARRIER + sex_inlast30days, data = Fake_cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = No)

#factorise
Fake_cccu_complete1$exclusion_R1<-as.factor(Fake_cccu_complete1$exclusion_R1)

#plot

plot(Fake_cccu_complete1$exclusion_R1)


#create df: exclude women following exclusion_R1 from the maindf 

Fake_cccu_R1 <-Fake_cccu_complete1 %>%
  filter(exclusion_R1 != 1) 

#check

table(Fake_cccu_R1$exclusion_R1) # :)


```


•	- Robustheitsanalyse 2:
•	Hauptausschluss + no contraception method in last 30 days + sex in last 30 days


##5.2 Analysis of robustness 2

```{r}
#overview over relevant variables

table(Fake_cccu_complete1$NOBARRIER)#no non-hormonal contraceptive method in last 30days
table(Fake_cccu_complete1$hc)#no hormonal contracepive method 
#joint = no contraceptive method 

table(Fake_cccu_complete1$sex_inlast30days)# yes= sex in last 30 days

#create column that indicates with 1 = sex and no contraceptive method used in last 30 days

Fake_cccu_complete1 <- Fake_cccu_complete1 %>%
  mutate(exclusion_R2 = ifelse(NOBARRIER == "(1) Yes" & 
                                 hc == "non_hc" &
                                 sex_inlast30days == "Yes",1,0))

table(Fake_cccu_complete1$exclusion_R2)

crosstabs(~exclusion_R1 + hc + NOBARRIER + sex_inlast30days, data = Fake_cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = Yes)

#factorise
Fake_cccu_complete1$exclusion_R2<-as.factor(Fake_cccu_complete1$exclusion_R2)

#plot

plot(Fake_cccu_complete1$exclusion_R2)

#create df: exclude women following exclusion_R2 from the maindf 

Fake_cccu_R2 <-Fake_cccu_complete1 %>%
  filter(exclusion_R2 != 1) 

#check

table(Fake_cccu_R2$exclusion_R2) # :)



```





##5.3 Analysis of robustness 3
 Used Vasectomy as contraceptive method
```{r}
#overview

table(Fake_cccu_complete1$VASECTOMY)
table(Fake_cccu_complete1$SP1VAS)
table(Fake_cccu_complete1$SP2VAS)


#create column that indicates if used Vasectomy

Fake_cccu_complete1 <- Fake_cccu_complete1 %>%
  mutate(exclusion_used_vasectomy = ifelse(VASECTOMY == "(1) Yes" |
                                             SP1VAS == "(1) Yes"|
                                             SP2VAS == "(1) Yes",1,0))


table(Fake_cccu_complete1$exclusion_used_vasectomy)

#factorize and plot

Fake_cccu_complete1$exclusion_used_vasectomy<-as.factor(Fake_cccu_complete1$exclusion_used_vasectomy)


plot(Fake_cccu_complete1$exclusion_used_vasectomy)

```



