---
title: "03_Exclusion"
author: "Chiara Draxler"
date: "29 3 2022"
output: html_document
---
#1. Load Data
```{r}

load("cccu_complete1.RData")
```

#2. Load Packages

```{r}
library(dplyr)
library(formr)
library(ggplot2)
```

#3. Full Dataset
```{r}
nrow(cccu_complete1) #timepoints
length(unique(cccu_complete1$CASEID)) #women

```

##3.1 Exclude t4 from df (bc. not necessary)

```{r}
cccu_complete1 <- cccu_complete1 %>%
  filter(WAVE != "t4")
```



# 4 Building columns that indicate exclusion from df
1 = yes 

## 4.1 Missing Main Predictor: HC
Dont exclude current IUD & non-hormonal

```{r}
table(cccu_complete1$hc)
table(is.na(cccu_complete1$hc))

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_predHC = ifelse(is.na(hc), 1, 0))

table(cccu_complete1$exclusion_missing_predHC)
cccu_complete1$exclusion_missing_predHC <- as.factor(cccu_complete1$exclusion_missing_predHC)
qplot(cccu_complete1$exclusion_missing_predHC)

x = cccu_complete1 %>%
  select(hc, exclusion_missing_predHC)
```

## 4.2 Missing Main Predictor: Satisfaction with HC

###dealing with high missingness because of simulation (so that models in analyses run)

!!!!NEEDS TO BE REMOVED!!
```{r}

#cccu_complete1$contra_satis = ifelse(is.na(cccu_complete1$contra_satis),1,cccu_complete1$contra_satis)

#table(is.na(cccu_complete1$contra_satis))

```

```{r}
table(cccu_complete1$contra_satis) 
table(is.na(cccu_complete1$contra_satis))

crosstabs( ~ is.na(contra_satis) + WAVE, data = cccu_complete1)

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_pred_contra_satis = ifelse(is.na(contra_satis), 1, 0))

table(cccu_complete1$exclusion_missing_pred_contra_satis)
cccu_complete1$exclusion_missing_pred_contra_satis <- as.factor(cccu_complete1$exclusion_missing_pred_contra_satis)
qplot(cccu_complete1$exclusion_missing_pred_contra_satis)

x = cccu_complete1 %>%
  select(contra_satis, exclusion_missing_pred_contra_satis)
```


## 4.3 Missing Main Predictor: Sex Freq & Sex Sat

```{r}
#sex freq
table(cccu_complete1$sex_freq)
table(is.na(cccu_complete1$sex_freq))

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_pred_sex_freq= ifelse(is.na(sex_freq), 1, 0))

table(cccu_complete1$exclusion_missing_pred_sex_freq)
cccu_complete1$exclusion_missing_pred_sex_freq <- as.factor(cccu_complete1$exclusion_missing_pred_sex_freq)
qplot(cccu_complete1$exclusion_missing_pred_sex_freq)

x = cccu_complete1 %>%
  select(sex_freq, exclusion_missing_pred_sex_freq)

#sex_sat
table(cccu_complete1$sexual_satisfaction)
table(is.na(cccu_complete1$sexual_satisfaction))

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_pred_sex_sat= ifelse(is.na(sexual_satisfaction), 1, 0))

crosstabs( ~ is.na(sexual_satisfaction) + rel_dur_factor, data = cccu_complete1)


table(cccu_complete1$exclusion_missing_pred_sex_sat)#high missingness
cccu_complete1$exclusion_missing_pred_sex_sat <- as.factor(cccu_complete1$exclusion_missing_pred_sex_sat)
qplot(cccu_complete1$exclusion_missing_pred_sex_sat)

x = cccu_complete1 %>%
  select(sexual_satisfaction, exclusion_missing_pred_sex_sat)

```

## 4.4 Missing Selection Predictors
```{r}
#Age
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_age = as.factor(ifelse(is.na(AGE),1,0)))

table(is.na(cccu_complete1$AGE))
table(cccu_complete1$exclusion_missing_selection_age)
    
#Degree
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_degree = as.factor(ifelse(is.na(DEGREE_recode),1,0))) 
                                                             
table(is.na(cccu_complete1$DEGREE_recode)) 
table(cccu_complete1$exclusion_missing_selection_degree)

#Povrate
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_povrate= as.factor(ifelse(is.na(POVRATE),1,0))) 

table(is.na(cccu_complete1$POVRATE))
table(cccu_complete1$exclusion_missing_selection_povrate)

#Healthproblems
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_healthprb= as.factor(ifelse(is.na(HLTHPROB_recode),1,0))) 

table(is.na(cccu_complete1$HLTHPROB_recode))
table(cccu_complete1$exclusion_missing_selection_healthprb)#high missings

#Med Problems
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_medprob= as.factor(ifelse(is.na(MEDPROB_recode),1,0))) 

table(is.na(cccu_complete1$MEDPROB_recode))
table(cccu_complete1$exclusion_missing_selection_medprob)

#Gaps in insurance
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_gapins= as.factor(ifelse(is.na(GAPINS_recode),1,0))) 

table(is.na(cccu_complete1$GAPINS_recode))
table(cccu_complete1$exclusion_missing_selection_gapins)#missings

#Type of insurance
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_typeins= as.factor(ifelse(is.na(TYPEINS_recode),1,0))) 

table(is.na(cccu_complete1$TYPEINS_recode))
table(cccu_complete1$exclusion_missing_selection_typeins)#missings

#N Kids at T1
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_nkids= as.factor(ifelse(is.na(NKIDS_t1),1,0))) 

table(is.na(cccu_complete1$NKIDS_t1))
table(cccu_complete1$exclusion_missing_selection_nkids)#missings

#pregnant between waves
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_preg_bet_waves= as.factor(ifelse(is.na(pregnant_between_waves),1,0))) 

table(is.na(cccu_complete1$pregnant_between_waves))
table(cccu_complete1$exclusion_missing_selection_preg_bet_waves)#missings


#had baby between waves
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_baby_bet_waves= as.factor(ifelse(is.na(had_baby_between_waves),1,0))) 

table(is.na(cccu_complete1$had_baby_between_waves))
table(cccu_complete1$exclusion_missing_selection_baby_bet_waves)#missings


#Feel about pregnancy
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_feelpg= as.factor(ifelse(is.na(FEELPG_recode),1,0))) 

table(is.na(cccu_complete1$FEELPG_recode))
table(cccu_complete1$exclusion_missing_selection_feelpg)#high missings

#Avoidance of pregnancy
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_avoid= as.factor(ifelse(is.na(Avoid_r),1,0))) 

table(is.na(cccu_complete1$Avoid_r))
table(cccu_complete1$exclusion_missing_selection_avoid)#high missings

#Relationship duration
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_selection_reldur= as.factor(ifelse(is.na(rel_dur_factor),1,0))) 

table(is.na(cccu_complete1$rel_dur_factor))
table(cccu_complete1$exclusion_missing_selection_reldur)



#complete exclusion for all selection variables
cccu_complete1 <- cccu_complete1 %>% mutate(exclusion_missing_selection = as.factor(ifelse(is.na(AGE) | is.na(DEGREE_recode) | is.na(POVRATE)| is.na(HLTHPROB_recode) | is.na(MEDPROB_recode)| is.na(GAPINS_recode) | is.na(TYPEINS_recode) | is.na(NKIDS_t1) |is.na(pregnant_between_waves) | is.na(had_baby_between_waves) | is.na(FEELPG_recode) | is.na(Avoid_r) | is.na(rel_dur_factor), 1, 0)))

qplot(cccu_complete1$exclusion_missing_selection)
table(cccu_complete1$exclusion_missing_selection)

x = cccu_complete1 %>%
  select(exclusion_missing_selection, exclusion_missing_selection_age, exclusion_missing_selection_degree, exclusion_missing_selection_povrate, exclusion_missing_selection_healthprb, exclusion_missing_selection_medprob, exclusion_missing_selection_gapins, exclusion_missing_selection_typeins, exclusion_missing_selection_nkids, exclusion_missing_selection_preg_bet_waves, exclusion_missing_selection_baby_bet_waves, exclusion_missing_selection_feelpg, exclusion_missing_selection_avoid, exclusion_missing_selection_reldur)
```


## 4.5 Missing Outcome (switch)
Dont exclude next IUD & non-hormonal
```{r}
table(cccu_complete1$switch)
table(is.na(cccu_complete1$switch))#high missingness


crosstabs( ~ is.na(switch) + WAVE, data = cccu_complete1)

cccu_complete1 %>% select(CASEID, WAVE, hc, hc_next, switch) %>% View()

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_outc_switch= ifelse(is.na(switch), 1, 0))

table(cccu_complete1$exclusion_missing_outc_switch)
cccu_complete1$exclusion_missing_outc_switch <- as.factor(cccu_complete1$exclusion_missing_outc_switch)

qplot(cccu_complete1$exclusion_missing_outc_switch)


x = cccu_complete1 %>%
  select(switch, exclusion_missing_outc_switch)

```


## 4.6 Emergency contraception
```{r}
#overview

table(cccu_complete1$EC_recode)

#create column that indicates if used EC

cccu_complete1 <- cccu_complete1 %>%
  mutate(exclusion_used_EC = ifelse(is.na(EC_recode), 0,
                                    ifelse(EC_recode == "No", 0,
                                           ifelse(EC_recode == "Yes", 1, NA))))

table(cccu_complete1$exclusion_used_EC)
cccu_complete1$exclusion_used_EC<- as.factor(cccu_complete1$exclusion_used_EC)
qplot(cccu_complete1$exclusion_used_EC)

```

## 4.7 IUD & Non-Hormonal
```{r}
table(cccu_complete1$hc)
table(cccu_complete1$IUD)

#IUD & non-hormonal 
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_IUD = ifelse(hc == "IUD&non_hc", 1,0)) 

table(cccu_complete1$IUD)
table(cccu_complete1$exclusion_IUD)
table(is.na(cccu_complete1$exclusion_IUD))


table(cccu_complete1$exclusion_IUD)
cccu_complete1$exclusion_IUD<- as.factor(cccu_complete1$exclusion_IUD)
qplot(cccu_complete1$exclusion_IUD)

x = cccu_complete1 %>%
  select(IUD, hc, exclusion_IUD)



#IUD_next & non-hormonal 

table(cccu_complete1$hc_next)
cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_IUD_next = ifelse(is.na(hc_next), 0,
                                    ifelse(hc_next == "non_hc" | hc_next == "hc", 0,
                                           ifelse(hc_next == "IUD&non_hc", 1, NA))))

table(cccu_complete1$exclusion_IUD_next)
table(is.na(cccu_complete1$exclusion_IUD_next))


table(cccu_complete1$exclusion_IUD_next)
cccu_complete1$exclusion_IUD_next<- as.factor(cccu_complete1$exclusion_IUD_next)
qplot(cccu_complete1$exclusion_IUD_next) #NA (missings) should be removed when excluding for missigness in hc or switch


x = cccu_complete1 %>%
  select(CASEID, WAVE, IUD_next, hc_next, exclusion_IUD_next)
```
#column for complete exclusion process of main analysis
```{r}
#create column for complete exclusion process 
cccu_complete1 <- cccu_complete1 %>% mutate(exclusion_complete = as.factor(ifelse(exclusion_missing_predHC == 1 | exclusion_missing_pred_contra_satis ==1 | exclusion_missing_pred_sex_freq ==1 | exclusion_missing_pred_sex_sat ==1 | exclusion_missing_selection ==1 | exclusion_missing_outc_switch ==1 | exclusion_used_EC ==1| exclusion_IUD ==1 | exclusion_IUD_next ==1, 1, 0)))
```


## 4.8 Subanalyses Duration
### 4.8.1 non-hormonal contra
```{r}
table(cccu_complete1$hc)

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_used_non_hc= ifelse(hc == "non_hc", 1,0))

table(cccu_complete1$exclusion_used_non_hc)
table(is.na(cccu_complete1$exclusion_used_non_hc))

cccu_complete1$exclusion_used_non_hc<- as.factor(cccu_complete1$exclusion_used_non_hc)
qplot(cccu_complete1$exclusion_used_non_hc)


```

### 4.8.2 unknow duration

####dealing with high missingness because of simulation (so that models run)
NEEDS TO BE REMOVED!
```{r}
#table(is.na(cccu_complete1$hc_dur))

#cccu_complete1$hc_dur = ifelse(is.na(cccu_complete1$hc_dur),1,cccu_complete1$hc_dur)

#table(is.na(cccu_complete1$hc_dur))
```


```{r}
table(cccu_complete1$hc_dur)
table(is.na(cccu_complete1$hc_dur))

crosstabs( ~ is.na(hc_dur) + sex_inlast30days, data = cccu_complete1)

cccu_complete1 <- cccu_complete1 %>%
 mutate(exclusion_missing_pred_hc_dur= ifelse(is.na(hc_dur), 1, 0))

table(cccu_complete1$exclusion_missing_pred_hc_dur)
cccu_complete1$exclusion_missing_pred_hc_dur<- as.factor(cccu_complete1$exclusion_missing_pred_hc_dur)
qplot(cccu_complete1$exclusion_missing_pred_hc_dur)

x = cccu_complete1 %>%
  select(hc_dur, exclusion_missing_pred_hc_dur)

```


## 4.9 Robustness analyses
### 4.9.1. No sex 
```{r}
table(cccu_complete1$sex_inlast30days)#no sex in last 30 days

#create column that indicates with 1 = no sex and no contraceptive method used in last 30 days

cccu_complete1 <- cccu_complete1 %>%
  mutate(exclusion_R1 = ifelse(is.na(sex_inlast30days), 0, 
                               ifelse(sex_inlast30days == "No", 1,
                                      ifelse(sex_inlast30days == "Yes", 0, NA))))

table(is.na(cccu_complete1$exclusion_R1))
cccu_complete1$exclusion_R1 <-as.factor(cccu_complete1$exclusion_R1)
qplot(cccu_complete1$exclusion_R1)#missingness might be because sex_inlast30days and NOBARRIER can be missing 

crosstabs(~hc + sex_inlast30days, data =cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = No)

crosstabs(~exclusion_R1 + hc + NOBARRIER + sex_inlast30days, data =cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = No)

```

### 4.9.2. Sex + no contra

```{r}
#overview over relevant variables

table(cccu_complete1$NOBARRIER)#no non-hormonal contraceptive method in last 30days
table(cccu_complete1$hc)#no hormonal contraceptive method 
#joint = no contraceptive method 

table(cccu_complete1$sex_inlast30days)# yes= sex in last 30 days

#create column that indicates with 1 = sex and no contraceptive method used in last 30 days

cccu_complete1 <- cccu_complete1 %>%
  mutate(exclusion_R2 = ifelse(is.na(NOBARRIER), 0,
                               ifelse(NOBARRIER == "(1) Yes" & 
                                 hc == "non_hc" &
                                 sex_inlast30days == "Yes",1,0)))

table(cccu_complete1$exclusion_R2)


cccu_complete1$exclusion_R2 <-as.factor(cccu_complete1$exclusion_R2)
qplot(cccu_complete1$exclusion_R2)#missingness might be because sex_inlast30days and NOBARRIER can be missing 

crosstabs(~is.na(exclusion_R2) + NOBARRIER + sex_inlast30days, data = cccu_complete1) #seems to have worked :) :) (see NOBARRIER = (1) Yes, sex_inlast30days = Yes)

```

### 4.9.3. Vasectomy
```{r}
#overview

table(cccu_complete1$VASECTOMY)
table(cccu_complete1$SP1VAS)
table(cccu_complete1$SP2VAS)



#create column that indicates if used Vasectomy
cccu_complete1 <- cccu_complete1 %>%
  mutate(exclusion_R3 = ifelse(VASECTOMY == "(1) Yes" |
                                 SP1VAS == "(1) Yes" | SP2VAS == "(1) Yes", 1, NA),
         exclusion_R3 = ifelse(is.na(exclusion_R3), 0, exclusion_R3))
         

table(cccu_complete1$exclusion_R3)
crosstabs(~exclusion_R3+ SP2VAS, data = cccu_complete1)
cccu_complete1$exclusion_R3 <-as.factor(cccu_complete1$exclusion_R3)
qplot(cccu_complete1$exclusion_R3)

```



# 5 Stepwise exclusion
## 5.1 Missing Main Predictor: HC
Dont exclude current IUD & non-hormonal
```{r}

#number of observations 
table(cccu_complete1$exclusion_missing_predHC)

#exclude from df

cccu_complete2 <-cccu_complete1 %>%
  filter(exclusion_missing_predHC !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_predHC = 1 (might be combination with other exclusion criteria)
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_predHC !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow() 

#0
```


## 5.2 Missing Main Predictor: Satisfaction with HC
```{r}
#overview number of observations
table(cccu_complete1$exclusion_missing_pred_contra_satis)

#exclude from df
cccu_complete3 <-cccu_complete2 %>%
  filter(exclusion_missing_pred_contra_satis !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_pred_contra_satis = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_pred_contra_satis !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#1188#high exclusion
```


## 5.3 Missing Main Predictor: Sex Freq & Sex Sat

```{r}

#sex freq

#overview number of observations
table(cccu_complete1$exclusion_missing_pred_sex_freq)

#exclude from df
cccu_complete4 <-cccu_complete3 %>%
  filter(exclusion_missing_pred_sex_freq !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_pred_sex_freq = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_pred_sex_freq !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#20

#sex satis
table(cccu_complete1$exclusion_missing_pred_sex_sat)


#exclude from df
cccu_complete5 <-cccu_complete4 %>%
  filter(exclusion_missing_pred_sex_sat !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_pred_sex_sat = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_pred_sex_sat !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#469#high exclusion
```

## 5.4 Missing Selection Predictors
```{r}

#overview
table(cccu_complete1$exclusion_missing_selection)

#exclude from df
cccu_complete6 <-cccu_complete5 %>%
  filter(exclusion_missing_selection !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_selection = 1 (might be combination with other exclusion criteria)

#for alle selection predictors

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()

#306


#separate for all selection predictors:
#Age
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_age !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Degree
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_degree !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Povrate
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_povrate !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Hlthprob
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_healthprb !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#266#relatively high exclusion

#MedProb
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_medprob !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0

#Gapins
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_gapins !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#24

#Typeins
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_typeins !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#24

#N kids at t1
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_nkids !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#15


#Preg between waves
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_preg_bet_waves !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#6

#baby between waves
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_baby_bet_waves !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#6

#Feelpg
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_feelpg !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#16

#Avoid
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_avoid !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#14

#rel dur
length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_selection_reldur !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0
```


## 5.5 Missing Outcome (switch)
Dont exclude next IUD & non-hormonal
```{r}
table(cccu_complete1$exclusion_missing_outc_switch)

#exclude from df
cccu_complete7 <-cccu_complete6 %>%
  filter(exclusion_missing_outc_switch !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_outc_switch = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_outc_switch !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#1427#high exclusion!



```

## 5.6 Emergency contraception
```{r}
table(cccu_complete1$exclusion_used_EC)

#exclude from df
cccu_complete8 <-cccu_complete7 %>%
  filter(exclusion_used_EC !=1)

#number of excluded women from cccu_complete1 bc of exclusion_used_EC = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_used_EC !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()#0
```


## 5.7 IUD & Non-Hormonal
```{r}
#IUD 
table(cccu_complete1$exclusion_IUD)

#exclude from df
cccu_complete9 <-cccu_complete8 %>%
  filter(exclusion_IUD !=1)

#number of excluded women from cccu_complete1 bc of exclusion_IUD = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_IUD !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#402

#IUD next

table(cccu_complete1$exclusion_IUD_next)

#exclude from df
cccu_complete10 <-cccu_complete9 %>%
  filter(exclusion_IUD_next !=1)

#number of excluded women from cccu_complete1 bc of exclusion_IUD_next = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_IUD_next !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#135

```

#rename df for Main Analysis 
```{r}
cccu_MA <- cccu_complete10
```


#save excluded sample for comparison included (cccu_MA) vs excluded sample (cccu_excluded)
```{r}
#save excluded sample 
cccu_excluded <-cccu_complete1 %>%
  filter(exclusion_complete ==1)

```


## 5.8 Subanalyses Duration
### 5.8.1 non-hormonal contra
```{r}
table(cccu_complete1$exclusion_used_non_hc)


#exclude from df
cccu_SA1 <-cccu_MA %>%
  filter(exclusion_used_non_hc !=1)

#number of excluded women from cccu_complete1 bc of exclusion_used_non_hc = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_used_non_hc !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#2079#high exclusion
```

### 5.8.2 unknow duration
```{r}
table(cccu_complete1$exclusion_missing_pred_hc_dur)

#exclude from df
cccu_SA <-cccu_SA1 %>%
  filter(exclusion_missing_pred_hc_dur !=1)

#number of excluded women from cccu_complete1 bc of exclusion_missing_pred_hc_dur = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_missing_pred_hc_dur !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#2580#high exclusion
```

## 5.9 Robustness analyses
### 5.9.1. No sex + no contra
```{r}
table(cccu_complete1$exclusion_R1)
#exclude from df
cccu_R1<-cccu_MA %>%
  filter(exclusion_R1 !=1)

#number of excluded women from cccu_complete1 bc of exclusion_R1 = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_R1 !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#656#relatively high exclusion

#df for subanalysis
cccu_R1_s<-cccu_SA %>%
  filter(exclusion_R1 !=1)

```

### 5.9.2. Sex + no contra

```{r}
table(cccu_complete1$exclusion_R2)
#exclude from df
cccu_R2<-cccu_MA %>%
  filter(exclusion_R2 !=1)

#number of excluded women from cccu_complete1 bc of exclusion_R2 = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_R2 !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#325#relatively high exclusion

#df for SA
cccu_R2_s<-cccu_SA %>%
  filter(exclusion_R2 !=1)

```

### 5.9.3. Vasectomy
```{r}
table(cccu_complete1$exclusion_R3)
#exclude from df
cccu_R3<-cccu_MA %>%
  filter(exclusion_R3 !=1)

#number of excluded women from cccu_complete1 bc of exclusion_R3 = 1 (might be combination with other exclusion criteria)

length(unique(cccu_complete1$CASEID)) -
  cccu_complete1 %>%
  filter(exclusion_R3 !=1) %>%
  select(CASEID) %>%
  unique() %>%
  nrow()
#1

#df for subanalysis
cccu_R3_s<-cccu_SA %>%
  filter(exclusion_R3 !=1)
```



#6 Save df

```{r}

#Main Analysis 

save(cccu_MA,file = "cccu_MA.RData")

load("cccu_MA.RData")


#Sub Analysis
save(cccu_SA,file = "cccu_SA.RData")

load("cccu_SA.RData")

#R1
##MA
save(cccu_R1,file = "cccu_R1.RData")

load("cccu_R1.RData")

##SA
save(cccu_R1_s,file = "cccu_R1_s.RData")

load("cccu_R1_s.RData")

#R2
##MA
save(cccu_R2,file = "cccu_R2.RData")

load("cccu_R2.RData")
##SA

save(cccu_R2_s,file = "cccu_R2_s.RData")

load("cccu_R2_s.RData")

#R3
##MA
save(cccu_R3,file = "cccu_R3.RData")

load("cccu_R3.RData")

##SA
save(cccu_R3_s,file = "cccu_R3_s.RData")

load("cccu_R3_s.RData")
```

