---
title: "04_Codebook"
author: "Chiara Draxler"
date: "31 5 2022"
output: html_document
---

##Introduction for working code:

0. Select a folder specific for the R project and define to use the folder for the R project constantly (when downloading the code from GitHub the folder will be hc_switch_cccu-main)

1. Download data from 
https://www.icpsr.umich.edu/web/DSDR/studies/37067/datadocumentation

--> Click on Download, then select R, then follow the login
--> store data in the folder specific to the R project in an extra sub-folder called RData (i.e., hc_switch_cccu-main - > RData)

--> Within the RData folder store data for wave 1 in DS0001, for wave 2 in DS0002 and so on  (i.e., hc_switch_cccu-main - > RData -> DS0001 )

--> name the Rdata files according to the wave: 

Wave 1: 37067-0001-Data (i.e., hc_switch_cccu-main - > RData -> DS0001 -> 37067-0001-Data.rda )

Wave 2: 37067-0002-Data (i.e., hc_switch_cccu-main - > RData -> DS0002 -> 37067-0002-Data.rda )


Wave 3: 37067-0003-Data (i.e., hc_switch_cccu-main - > RData -> DS0003 -> 37067-0003-Data.rda )


Wave 4: 37067-0004-Data (i.e., hc_switch_cccu-main - > RData -> DS0004 -> 37067-0004-Data.rda )


--> attention to the .rda ending when loading the data into R!

2. make sure to install all relevant packages before running the code!

All relevant packages and versions can be seen in the section "Analyses"

3. run the code according to the defined order beginning with 01_ (or 0 if you want to have a look at the synthetic data) and ending with 09_ so that all data frames are created appropriately

4. Run  the Code :) 

# Codebook {.tabset}
## 1. Packages and df
```{r}
library(ggplot2)
theme_set(theme_bw())
library(codebook)
library(tidyverse)
library(future)
library(psych)
library(Hmisc)
load("cccu_MA.RData")
```

## 2. Select data
```{r}
cccu_MA = cccu_MA %>%
  select(WAVE, switch, hc, contra_satis, hc_dur, sexual_satisfaction, sex_freq,
         AGE, DEGREE_recode, POVRATE, HLTHPROB_recode, MEDPROB_recode, GAPINS_recode, TYPEINS_recode, NKIDS_t1, pregnant_between_waves, had_baby_between_waves, Avoid_r, FEELPG_recode, rel_dur_factor)
```

## 3. Codebook
```{r}
codebook(cccu_MA, missingness_report = FALSE, indent = "###")
```



#Plots


#Correlations

```{r}
#for t1
cccu_MA_t1 <- cccu_MA%>%
  filter(WAVE == "t1")
cccu_MA_t1_correlations <- cccu_MA_t1 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)


pairs.panels(cccu_MA_t1_correlations, cex.cor = 10)

rcorr(as.matrix(cccu_MA_t1_correlations))


#for t2
cccu_MA_t2 <- cccu_MA%>%
  filter(WAVE == "t2")

cccu_MA_t2_correlations <- cccu_MA_t2 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)
pairs.panels(cccu_MA_t2_correlations, cex.cor = 10)
rcorr(as.matrix(cccu_MA_t2_correlations))

#for t3
cccu_MA_t3 <- cccu_MA%>%
  filter(WAVE == "t3")

cccu_MA_t3_correlations <- cccu_MA_t3 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)

pairs.panels(cccu_MA_t3_correlations, cex.cor = 10)

rcorr(as.matrix(cccu_MA_t3_correlations))
```

