---
title: "05_Descriptives"
author: "Chiara Draxler"
date: "24 1 2022"
output: html_document
---

#Introduction for working code:

0. Download the Code from Github. The new downloaded folder hc_switch_cccu-main contains the R project, Rmd Code, created data frames, knitted Html Code, Figures as .pdf and.jpg, Preregistered synthetic Code, and a folder to store the downloaded RData called RData.

Name the folder appropriately (when downloading the code from GitHub the folder will be hc_switch_cccu-main).

1. Download data from 
https://www.icpsr.umich.edu/web/DSDR/studies/37067/datadocumentation

Attention! The downloaded project from GitHub does not contain any data files!

--> Click on Download, then select R, then follow the login
--> store data in the folder specific to the R project in an extra sub-folder called RData (i.e., hc_switch_cccu-main - > RData). If you downloaded the code from GitHub, the RData folder will be already in the hc_switch_cccu-main projects folder.  

--> Within the RData folder store data for wave 1 in DS0001, for wave 2 in DS0002 and so on  (i.e., hc_switch_cccu-main - > RData -> DS0001 ). If you downloaded the code from GitHub, the relevant folders will be already there.

--> name the Rdata files according to the wave: 

Wave 1: 37067-0001-Data (i.e., hc_switch_cccu-main - > RData -> DS0001 -> 37067-0001-Data.rda )

Wave 2: 37067-0002-Data (i.e., hc_switch_cccu-main - > RData -> DS0002 -> 37067-0002-Data.rda )


Wave 3: 37067-0003-Data (i.e., hc_switch_cccu-main - > RData -> DS0003 -> 37067-0003-Data.rda )


Wave 4: 37067-0004-Data (i.e., hc_switch_cccu-main - > RData -> DS0004 -> 37067-0004-Data.rda )


--> attention to the .rda ending when loading the data into R!

2. make sure to install all relevant packages before running the code!

All relevant packages and versions can be seen in the section "Analyses"

3. run the code according to the defined order beginning with 01_ (or 0 if you want to have a look at the synthetic data) and ending with 09_ so that all data frames are created appropriately

4. Run  the Code :) 

#1. load Data
```{r}
load("cccu_MA.RData")
load("cccu_excluded.RData")
```


#2. Load Packages
```{r}
library(psych)
library(dplyr)
library(rstatix)
library(ufs)
library(Hmisc)


```



#3. Participants
##filter values for waves

```{r}
cccu_MA_t1 <- cccu_MA%>%
  filter(WAVE == "t1")

cccu_MA_t2 <- cccu_MA%>%
  filter(WAVE == "t2")

cccu_MA_t3 <- cccu_MA%>%
  filter(WAVE == "t3")

cccu_MA_t4 <- cccu_MA%>%
  filter(WAVE == "t4")
```
##hormonal vs. non hormonal contraception 
```{r}
table(cccu_MA_t1$hc)#IUD & non_hc should be zero bc of exclusion - yes
1032/1723

cccu_MA_t1_only_hc <- cccu_MA_t1 %>%
  filter(hc == "hc") %>%
  filter(CONDOMR != "(1) yes" | is.na(CONDOMR),
         VASECTOMY != "(1) yes" | is.na(VASECTOMY),
         WITHDRAWR != "(1) yes" | is.na(WITHDRAWR),
         NFPR != "(1) yes" | is.na(NFPR),
         SPERMR != "(1) yes" | is.na(SPERMR))

table(cccu_MA_t1_only_hc$PILL) # sum is 630 = hormonal users only
table(cccu_MA_t1_only_hc$PATCH)
table(cccu_MA_t1_only_hc$RING)
table(cccu_MA_t1_only_hc$DEPO)
table(cccu_MA_t1_only_hc$IMPLANT)
table(cccu_MA_t1_only_hc$IUD)

cccu_MA_t1_combi_hc <- cccu_MA_t1 %>%
  filter(hc == "hc") %>%
  filter(CONDOMR == "(1) yes" | 
           VASECTOMY == "(1) yes" |
           WITHDRAWR == "(1) yes" |
           NFPR == "(1) yes" | 
           SPERMR == "(1) yes")

table(cccu_MA_t1_combi_hc$PILL)
table(cccu_MA_t1_combi_hc$PATCH)
table(cccu_MA_t1_combi_hc$RING)
table(cccu_MA_t1_combi_hc$DEPO)
table(cccu_MA_t1_combi_hc$IMPLANT)
table(cccu_MA_t1_combi_hc$IUD)


cccu_MA_t1_non_hc <- cccu_MA_t1 %>%
  filter(hc == "non_hc")

table(cccu_MA_t1_non_hc$CONDOMR) # sum is n of non-hc users = 691
table(cccu_MA_t1_non_hc$VASECTOMY)
table(cccu_MA_t1_non_hc$WITHDRAWR)
table(cccu_MA_t1_non_hc$NFPR)
table(cccu_MA_t1_non_hc$SPERMR)
table(cccu_MA_t1_non_hc$NOBARRIER)

```

##Age
```{r}
#as.numeric
psych::describe(cccu_MA_t1$AGE)
table(cccu_MA_t1$AGE)
```
##Ethnicity

```{r}
table(cccu_MA_t1$Ethnicity)

1169/1723
275/1723

```


##Degree
```{r}
table(cccu_MA_t1$DEGREE_recode)

597/1723
432/1723


```
##Employment Status
```{r}
table(cccu_MA_t1$Employment_status)
1078/1723
81/1723
(12+186+26+340)/1723
12/564
186/564
26/564
340/564

12+186+26+340
```


##Relationship Status & Duration

```{r}
#status
table(cccu_MA_t1$partnered)
1293/1723

table(cccu_MA_t1$rel_dur_factor)

#duration
table(cccu_MA_t1$rel_dur)

psych::describe(cccu_MA_t1$rel_dur)

describe(cccu_MA_t1$rel_dur_years)
describe(cccu_MA_t1$rel_dur_months)
```


##Region and State
```{r}
#region
table(cccu_MA_t1$Region_recode)
548/1723
283/1723

#state
table(cccu_MA_t1$state_recode)
```



##Number of Kids
```{r}
table(cccu_MA_t1$NKIDS_t1)

936/1723
329/1723
304/1723

```


##Type of Insurance
```{r}
table(cccu_MA_t1$TYPEINS)
table(cccu_MA_t1$TYPEINS_recode)
1456/1723

```


##Income
```{r}
table(cccu_MA_t1$Income)
```

##POVRATE
```{r}
psych::describe(cccu_MA_t1$POVRATE)
table(cccu_MA_t1$POVRATE)

(2 +   3  +  1  +  4  +  3   +13 +   3 +   1 +  15  +  7 +   1 +   1  +  2+   21    +1    +1 +  12 +   1 +   7 + 4   + 2  + 11 +  11  +  7   + 1 +   5+    8  +  4 +  11  + 16  + 11 +   4  +  3 +   3 +  16 +   1  + 14   +18 + 4  +  1 +  10+    1  +  9  +  9  + 14 +   3+   13)/1723
```


#Comparision included to excluded sample 
```{r}
comp_inex = rbind(cccu_MA %>% mutate(exclude = "no"),
                     cccu_excluded %>% mutate(exclude = "yes"))
table(comp_inex$exclude)
```

##hc use
```{r}
chisq.test(comp_inex$hc, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$hc,comp_inex$exclude)
confIntV(comp_inex$hc,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$hc)
round(table(cccu_MA$hc)/3787, 2)
table(is.na(cccu_MA$hc))
table(is.na(cccu_MA$hc))/3787

table(cccu_excluded$hc)
round(table(cccu_excluded$hc)/6452, 2)
table(is.na(cccu_excluded$hc))
table(is.na(cccu_excluded$hc))/6452
```


##contraceptive satisfation
```{r}
t.test(comp_inex$contra_satis ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)


comp_inex %>% cohens_d(contra_satis ~ exclude, var.equal = TRUE, ci = TRUE)

psych::describe(cccu_MA$contra_satis)
psych::describe(cccu_excluded$contra_satis)
```


##sexual frequency
```{r}

chisq.test(comp_inex$sex_freq, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$sex_freq,comp_inex$exclude)
confIntV(comp_inex$sex_freq,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$sex_freq)
round(table(cccu_MA$sex_freq)/3787, 2)
table(is.na(cccu_MA$sex_freq))
table(is.na(cccu_MA$sex_freq))/3787

table(cccu_excluded$sex_freq)
2374+1879+1238+835+126
round(table(cccu_excluded$sex_freq)/6452, 2)
table(is.na(cccu_excluded$sex_freq))
table(is.na(cccu_excluded$sex_freq))/6452

```


##sexual satisfaction 
```{r}
t.test(comp_inex$sexual_satisfaction ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)

comp_inex %>% cohens_d(sexual_satisfaction ~ exclude, var.equal = TRUE, ci = TRUE)

psych::describe(cccu_MA$sexual_satisfaction)
psych::describe(cccu_excluded$sexual_satisfaction)

```


##Age
```{r}
t.test(comp_inex$AGE ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)

comp_inex %>% cohens_d(AGE ~ exclude, var.equal = TRUE, ci = TRUE)

psych::describe(cccu_MA$AGE)
psych::describe(cccu_excluded$AGE)
```


##Degree
```{r}
chisq.test(comp_inex$DEGREE_recode, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$DEGREE_recode,comp_inex$exclude)
confIntV(comp_inex$DEGREE_recode,comp_inex$exclude, conf.level = 0.95)


table(cccu_MA$DEGREE_recode)
round(table(cccu_MA$DEGREE_recode)/3787, 2)
table(is.na(cccu_MA$DEGREE_recode))
table(is.na(cccu_MA$DEGREE_recode))/3787

table(cccu_excluded$DEGREE_recode)
round(table(cccu_excluded$DEGREE_recode)/6452, 2)
table(is.na(cccu_excluded$DEGREE_recode))
table(is.na(cccu_excluded$DEGREE_recode))/6452
```


##Poverty
```{r}
t.test(comp_inex$POVRATE ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)

comp_inex %>% cohens_d(POVRATE ~ exclude, var.equal = TRUE, ci = TRUE)

psych::describe(cccu_MA$POVRATE)
psych::describe(cccu_excluded$POVRATE)
```


##Health problems
```{r}
chisq.test(comp_inex$HLTHPROB_recode, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$HLTHPROB_recode,comp_inex$exclude)
confIntV(comp_inex$HLTHPROB_recode,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$HLTHPROB_recode)
round(table(cccu_MA$HLTHPROB_recode)/3787, 2)
table(is.na(cccu_MA$HLTHPROB_recode))
table(is.na(cccu_MA$HLTHPROB_recode))/3787

table(cccu_excluded$HLTHPROB_recode)
round(table(cccu_excluded$HLTHPROB_recode)/6452, 2)
table(is.na(cccu_excluded$HLTHPROB_recode))
table(is.na(cccu_excluded$HLTHPROB_recode))/6452
```


##medical problems
```{r}
chisq.test(comp_inex$MEDPROB_recode, comp_inex$exclude, correct=FALSE)

cramersV(comp_inex$MEDPROB_recode,comp_inex$exclude)
confIntV(comp_inex$MEDPROB_recode,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$MEDPROB_recode)
round(table(cccu_MA$MEDPROB_recode)/3787, 2)
table(is.na(cccu_MA$MEDPROB_recode))
table(is.na(cccu_MA$MEDPROB_recode))/3787

table(cccu_excluded$MEDPROB_recode)
round(table(cccu_excluded$MEDPROB_recode)/6452, 2)
table(is.na(cccu_excluded$MEDPROB_recode))
table(is.na(cccu_excluded$MEDPROB_recode))/6452
```


##gaps in insurance
```{r}
chisq.test(comp_inex$GAPINS_recode, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$GAPINS_recode,comp_inex$exclude)
confIntV(comp_inex$GAPINS_recode,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$GAPINS_recode)
round(table(cccu_MA$GAPINS_recode)/3787, 2)
table(is.na(cccu_MA$GAPINS_recode))
table(is.na(cccu_MA$GAPINS_recode))/3787

table(cccu_excluded$GAPINS_recode)
round(table(cccu_excluded$GAPINS_recode)/6452, 2)
table(is.na(cccu_excluded$MEDPROB_recode))
table(is.na(cccu_excluded$MEDPROB_recode))/6452
```

##insuranced?
```{r}
chisq.test(comp_inex$TYPEINS_recode, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$TYPEINS_recode,comp_inex$exclude)
confIntV(comp_inex$TYPEINS_recode,comp_inex$exclude, conf.level = 0.95)


table(cccu_MA$TYPEINS_recode)
round(table(cccu_MA$TYPEINS_recode)/3787, 2)
table(is.na(cccu_MA$TYPEINS_recode))
table(is.na(cccu_MA$TYPEINS_recode))/3787

table(cccu_excluded$TYPEINS_recode)
round(table(cccu_excluded$TYPEINS_recode)/6452, 2)
table(is.na(cccu_excluded$TYPEINS_recode))
table(is.na(cccu_excluded$TYPEINS_recode))/6452
```


##number of kids at t1
```{r}
chisq.test(comp_inex$NKIDS_t1, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$NKIDS_t1,comp_inex$exclude)
confIntV(comp_inex$NKIDS_t1,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$NKIDS_t1)
round(table(cccu_MA$NKIDS_t1)/3787, 2)
table(is.na(cccu_MA$NKIDS_t1))
table(is.na(cccu_MA$NKIDS_t1))/3787

table(cccu_excluded$NKIDS_t1)
round(table(cccu_excluded$NKIDS_t1)/6452, 2)
table(is.na(cccu_excluded$NKIDS_t1))
table(is.na(cccu_excluded$NKIDS_t1))/6452

```


##pregnant between waves
```{r}
chisq.test(comp_inex$pregnant_between_waves, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$pregnant_between_waves,comp_inex$exclude)
confIntV(comp_inex$pregnant_between_waves,comp_inex$exclude, conf.level = 0.95)


table(cccu_MA$pregnant_between_waves)
round(table(cccu_MA$pregnant_between_waves)/3787, 2)
table(is.na(cccu_MA$pregnant_between_waves))
table(is.na(cccu_MA$pregnant_between_waves))/3787

table(cccu_excluded$pregnant_between_waves)
round(table(cccu_excluded$pregnant_between_waves)/6452, 2)
table(is.na(cccu_excluded$pregnant_between_waves))
table(is.na(cccu_excluded$pregnant_between_waves))/6452

```

##had baby between waves
```{r}
chisq.test(comp_inex$had_baby_between_waves, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$had_baby_between_waves,comp_inex$exclude)
confIntV(comp_inex$had_baby_between_waves,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$had_baby_between_waves)
round(table(cccu_MA$had_baby_between_waves)/3787, 2)
table(is.na(cccu_MA$had_baby_between_waves))
table(is.na(cccu_MA$had_baby_between_waves))/3787

table(cccu_excluded$had_baby_between_waves)
round(table(cccu_excluded$had_baby_between_waves)/6452, 2)
table(is.na(cccu_excluded$had_baby_between_waves))
table(is.na(cccu_excluded$had_baby_between_waves))/6452
```


##avoidance
```{r}
t.test(comp_inex$Avoid_r ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)

comp_inex %>% cohens_d(Avoid_r ~ exclude, var.equal = TRUE, ci = TRUE)


psych::describe(cccu_MA$Avoid_r)
psych::describe(cccu_excluded$Avoid_r)
```


##feelings about pregnancy
```{r}
t.test(comp_inex$FEELPG_recode ~ comp_inex$exclude,
       alternative = 'two.sided',
       paired = FALSE,
       conf.level = .95)

comp_inex %>% cohens_d(FEELPG_recode ~ exclude, var.equal = TRUE, ci = TRUE)
psych::describe(cccu_MA$FEELPG_recode)
psych::describe(cccu_excluded$FEELPG_recode)
```


##relationship duration
```{r}

chisq.test(comp_inex$rel_dur_factor, comp_inex$exclude, correct=FALSE)
cramersV(comp_inex$rel_dur_factor,comp_inex$exclude)
confIntV(comp_inex$rel_dur_factor,comp_inex$exclude, conf.level = 0.95)

table(cccu_MA$rel_dur_factor)
round(table(cccu_MA$rel_dur_factor)/3787, 2)
table(is.na(cccu_MA$rel_dur_factor))
table(is.na(cccu_MA$rel_dur_factor))/3787

table(cccu_excluded$rel_dur_factor)
round(table(cccu_excluded$rel_dur_factor)/6452, 2)
table(is.na(cccu_excluded$rel_dur_factor))
table(is.na(cccu_excluded$rel_dur_factor))/6452
```


#4. Descriptives of Variables
##t1
```{r}
cccu_MA_t1_descriptives <- cccu_MA_t1 %>%
  select(
    hc, switch, contra_satis, hc_dur,
    sexual_satisfaction, sex_freq,
    AGE, DEGREE_recode, POVRATE,
    HLTHPROB_recode, MEDPROB_recode,
    GAPINS_recode, TYPEINS_recode,
    NKIDS_t1, pregnant_between_waves, 
    had_baby_between_waves,
    Avoid_r, FEELPG_recode,
    rel_dur_factor)

psych::describe(cccu_MA_t1_descriptives$contra_satis)
psych::describe(cccu_MA_t1_descriptives$hc_dur)
psych::describe(cccu_MA_t1_descriptives$sexual_satisfaction)
psych::describe(cccu_MA_t1_descriptives$AGE)

psych::describe(cccu_MA_t1_descriptives$POVRATE)
psych::describe(cccu_MA_t1_descriptives$Avoid_r)


psych::describe(cccu_MA_t1_descriptives$FEELPG_recode)


table(cccu_MA_t1_descriptives$hc)
table(cccu_MA_t1_descriptives$switch)
table(cccu_MA_t1_descriptives$sex_freq)
table(cccu_MA_t1_descriptives$DEGREE_recode)
table(cccu_MA_t1_descriptives$HLTHPROB_recode)
table(cccu_MA_t1_descriptives$MEDPROB_recode)
table(cccu_MA_t1_descriptives$GAPINS_recode)
table(cccu_MA_t1_descriptives$TYPEINS_recode)
table(cccu_MA_t1_descriptives$NKIDS_t1)
table(cccu_MA_t1_descriptives$pregnant_between_waves)
table(cccu_MA_t1_descriptives$had_baby_between_waves)
table(cccu_MA_t1_descriptives$rel_dur_factor)

```
##t2
```{r}
cccu_MA_t2_descriptives <- cccu_MA_t2 %>%
  select(
    hc, switch, contra_satis, hc_dur,
    sexual_satisfaction, sex_freq,
    AGE, DEGREE_recode, POVRATE,
    HLTHPROB_recode, MEDPROB_recode,
    GAPINS_recode, TYPEINS_recode,
    NKIDS_t1, pregnant_between_waves, 
    had_baby_between_waves,
    Avoid_r, FEELPG_recode,
    rel_dur_factor)
colnames(cccu_MA_t2_descriptives)

psych::describe(cccu_MA_t2_descriptives$contra_satis)
psych::describe(cccu_MA_t2_descriptives$hc_dur)
psych::describe(cccu_MA_t2_descriptives$sexual_satisfaction)
psych::describe(cccu_MA_t2_descriptives$AGE)

psych::describe(cccu_MA_t2_descriptives$POVRATE)
psych::describe(cccu_MA_t2_descriptives$Avoid_r)


psych::describe(cccu_MA_t2_descriptives$FEELPG_recode)


table(cccu_MA_t2_descriptives$hc)
table(cccu_MA_t2_descriptives$switch)
table(cccu_MA_t2_descriptives$sex_freq)
table(cccu_MA_t2_descriptives$DEGREE_recode)
table(cccu_MA_t2_descriptives$HLTHPROB_recode)
table(cccu_MA_t2_descriptives$MEDPROB_recode)
table(cccu_MA_t2_descriptives$GAPINS_recode)
table(cccu_MA_t2_descriptives$TYPEINS_recode)
table(cccu_MA_t2_descriptives$NKIDS_t1)
table(cccu_MA_t2_descriptives$pregnant_between_waves)
table(cccu_MA_t2_descriptives$had_baby_between_waves)
table(cccu_MA_t2_descriptives$rel_dur_factor)

```

##t3
```{r}
cccu_MA_t3_descriptives <- cccu_MA_t3 %>%
  select(
    hc, switch, contra_satis, hc_dur,
    sexual_satisfaction, sex_freq,
    AGE, DEGREE_recode, POVRATE,
    HLTHPROB_recode, MEDPROB_recode,
    GAPINS_recode, TYPEINS_recode,
    NKIDS_t1, pregnant_between_waves, 
    had_baby_between_waves,
    Avoid_r, FEELPG_recode,
    rel_dur_factor)

psych::describe(cccu_MA_t3_descriptives$contra_satis)
psych::describe(cccu_MA_t3_descriptives$hc_dur)
psych::describe(cccu_MA_t3_descriptives$sexual_satisfaction)
psych::describe(cccu_MA_t3_descriptives$AGE)

psych::describe(cccu_MA_t3_descriptives$POVRATE)
psych::describe(cccu_MA_t3_descriptives$Avoid_r)


psych::describe(cccu_MA_t3_descriptives$FEELPG_recode)


table(cccu_MA_t3_descriptives$hc)
table(cccu_MA_t3_descriptives$switch)
table(cccu_MA_t3_descriptives$sex_freq)
table(cccu_MA_t3_descriptives$DEGREE_recode)
table(cccu_MA_t3_descriptives$HLTHPROB_recode)
table(cccu_MA_t3_descriptives$MEDPROB_recode)
table(cccu_MA_t3_descriptives$GAPINS_recode)
table(cccu_MA_t3_descriptives$TYPEINS_recode)
table(cccu_MA_t3_descriptives$NKIDS_t1)
table(cccu_MA_t3_descriptives$pregnant_between_waves)
table(cccu_MA_t3_descriptives$had_baby_between_waves)
table(cccu_MA_t3_descriptives$rel_dur_factor)
```


#5. Correlation Matrix
```{r}
#for t1
cccu_MA_t1_correlations <- cccu_MA_t1 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)

out <- corr.test(cccu_MA_t1_correlations)
print(out, short = FALSE)


#for t2


cccu_MA_t2_correlations <- cccu_MA_t2 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)
out <- corr.test(cccu_MA_t2_correlations)
print(out, short = FALSE)
#t3


cccu_MA_t3_correlations <- cccu_MA_t3 %>%
  select(contra_satis, hc_dur,
    sexual_satisfaction,
    AGE, POVRATE, Avoid_r, FEELPG_recode)

out <- corr.test(cccu_MA_t3_correlations)
print(out, short = FALSE)

```



#6. Checks for normality
```{r}
#hc use
table(cccu_MA$hc)
plot(cccu_MA$hc)

#contraceptive satisfaction
hist(cccu_MA$contra_satis) #no normal distribution
qqnorm(cccu_MA$contra_satis)
qqline(cccu_MA$contra_satis)

#contraceptive duration
hist(cccu_MA$hc_dur) #no normal distribution
qqnorm(cccu_MA$hc_dur)
qqline(cccu_MA$hc_dur)
table(cccu_MA$hc_dur)


#sexual satisfaction
hist(cccu_MA$sexual_satisfaction) #no normal distribution
qqnorm(cccu_MA$sexual_satisfaction)
qqline(cccu_MA$sexual_satisfaction)

#sexual frequency
table(cccu_MA$sex_freq)
plot(cccu_MA$sex_freq)#no sex und once relativ klein

#Age
hist(cccu_MA$AGE) #nearly no normal distribution
qqnorm(cccu_MA$AGE)
qqline(cccu_MA$AGE)

#degree
table(cccu_MA$DEGREE_recode)#no education bis 12. klasse sehr klein, ebenso doctoral degree
plot(cccu_MA$DEGREE_recode)

#Povrate
hist(cccu_MA$POVRATE) #no normal distribution
qqnorm(cccu_MA$POVRATE)
qqline(cccu_MA$POVRATE)

#health problems
table(cccu_MA$HLTHPROB_recode)#yes klein
plot(cccu_MA$HLTHPROB_recode)

#medical problems
table(cccu_MA$MEDPROB_recode)#yes klein
plot(cccu_MA$MEDPROB_recode)

#gaps in insurance
table(cccu_MA$GAPINS_recode)#yes klein
plot(cccu_MA$GAPINS_recode)

#insuranced
table(cccu_MA$TYPEINS_recode)#no klein
plot(cccu_MA$TYPEINS_recode)

#nkids t1
table(cccu_MA$NKIDS_t1)# 3 und 4 oder mehr Kinder klein
plot(cccu_MA$NKIDS_t1)

#pregnant / had baby between waves
table(cccu_MA$pregnant_between_waves)#yes klein
plot(cccu_MA$pregnant_between_waves)

table(cccu_MA$had_baby_between_waves)#yes klein
plot(cccu_MA$had_baby_between_waves)

#avoidance
hist(cccu_MA$Avoid_r) #no normal distribution
qqnorm(cccu_MA$Avoid_r)
qqline(cccu_MA$Avoid_r)

#feelings about pregnancy
hist(cccu_MA$FEELPG_recode) #no normal distribution
qqnorm(cccu_MA$FEELPG_recode)
qqline(cccu_MA$FEELPG_recode)

#relationship duration
table(cccu_MA$rel_dur_factor)
plot(cccu_MA$rel_dur_factor)
```


