---
title: "11_SubAnalysis_Models"
author: "Chiara Draxler"
date: "16 11 2022"
output: html_document
---
# 1. Load Packages
```{r}
library(brms)
library(marginaleffects)
library(tidyverse)


options(scipen = 999)

set.seed(180822)

set_priors <- c(prior(normal(0, 1), class = b),
                prior(normal(0, 1), class = sd))
```

# 2. Load Data
```{r}
load("cccu_MA.RData")

cccu_MA <- cccu_MA %>%
  arrange(CASEID) %>%
  mutate_if(is.factor, droplevels)
```

# Datawrangling
```{r}
cccu_MA <- cccu_MA %>%
  mutate(hc_dur = ifelse(hc == "non_hc",-9999, hc_dur))
```

# 3. Models

## 3.1 Model 1: including directly with contraceptive method associated predictors

DURATION and satisfaction!

```{r}
sa_m1 <- brm(
  switch ~ hc + hc:hc_dur + (1 | CASEID),
  family = bernoulli(),
  data = cccu_MA,
  prior = set_priors,
  file = "models/sa_m1_1.Rds"
)

summary(sa_m1, prob = .997)
```

## 3.2 Model 2: including directly with contraceptive method associated predictors

DURATION and satisfaction!

```{r}
sa_m2 <- brm(
  switch ~ hc * contra_satis + hc:hc_dur + hc:hc_dur:contra_satis + (1 | CASEID),
  family = bernoulli(),
  data = cccu_MA,
  prior = set_priors,
  file = "models/sa_m2_1.Rds"
)

summary(sa_m2, prob = .997)
```


## 3.3 Model 3: including not directly with contraceptive method associated predictors
```{r}
sa_m3 <-
  brm(
    switch ~ hc * contra_satis +  hc * sexual_satisfaction + hc * sex_freq + hc:hc_dur +
      hc:hc_dur:contra_satis +
      hc:hc_dur:sexual_satisfaction +
      hc:hc_dur:sex_freq +
      (1 | CASEID),
    family = bernoulli(),
    data = cccu_MA,
    prior = set_priors,
    file = "models/sa_m3_1.Rds"
  )

summary(sa_m3, prob = .997)
```

## 3.4 Model 4: Controlling for observed selection effects
```{r}
sa_m4 <-
  brm(
    switch ~ hc * contra_satis +  hc * sexual_satisfaction + hc * sex_freq +
      hc * AGE + hc * DEGREE_recode +
      hc * POVRATE +
      hc * HLTHPROB_recode + hc * MEDPROB_recode +  hc * GAPINS_recode +
      hc * TYPEINS_recode + hc * NKIDS_t1 +  hc * pregnant_between_waves +
      hc * had_baby_between_waves + hc * Avoid_r +
      hc * FEELPG_recode +
      hc * rel_dur_factor +
      hc:hc_dur +
      hc:hc_dur:contra_satis +
      hc:hc_dur:sexual_satisfaction +
      hc:hc_dur:sex_freq +
      hc:hc_dur:AGE +
      hc:hc_dur:DEGREE_recode +
      hc:hc_dur:POVRATE +
      hc:hc_dur:HLTHPROB_recode +
      hc:hc_dur:MEDPROB_recode +
      hc:hc_dur:GAPINS_recode +
      hc:hc_dur:TYPEINS_recode +
      hc:hc_dur:NKIDS_t1 +
      hc:hc_dur:pregnant_between_waves +
      hc:hc_dur:had_baby_between_waves +
      hc:hc_dur:Avoid_r +
      hc:hc_dur:FEELPG_recode +
      hc:hc_dur:rel_dur_factor +
      (1 | CASEID),
    family = bernoulli(),
    data = cccu_MA,
    prior = set_priors,
    file = "models/sa_m4_1.Rds"
  )

summary(sa_m4, prob = .997)
```


